### 2013-09-16 Reports/Report1/reviewedpapers.tex
.

\section{Overview On Reviewed Papers}
Since the defined problem in 2012 TREC Contextual Suggestion Track is some how similar to the current problem, I focused on reviewing the solution proposed by participants of this Track. In TREC Contextual Suggestion Track, different factors like personal preferences, location and time influence on ranking of venues. I have tried to concentrate on the way different papers have encountered with the ranking problem in order to gain some ideas for current problem.

Here is a short brief of some of them:

\subsection{CSIRO ICT Centre \cite{CSIRO}} 
Besides the solution presented for accumulating the data of venues, it offers a vector-space approach for identifying personal preferences. Armed with a preference vector for each profile, it scores each venue according to its cosine distance.

\subsection{Georgetown University \cite{GeorgetownUniversity}}
The represented solution for ranking seems very simple and straightforward. First, it creates a list of venues in different categories. Then based on scores for each category which is filled in user's profile, it sums per-user category scores with the scores for every venues in each category. Finally it returns the first top ten venues. Boosting well-known attractions, using learning techniques (SVMRank) for ranking venues in each category and defining a limit for each set are some special points in the paper.

\subsection{ICTNET \cite{ICTNET}}
The final formula for ranking consisted of some fixed factors which are selected using feedback method. Although the formula seems very clear and practical, the way to achieve the factors is not explained clearly.

\subsection{IRIT \cite{IRIT}}
I found the paper quite interesting as it acquired the first ranking between other participants.

### 2013-09-17 Reports/Report1/reviewedpapers.tex
finishing reviewed papers

@@
 I found the paper quite interesting as it acquired the first ranking between other participants.
+Like some other papers, they also create a Vector Space Model and calculate similarity based on cosine measure.
+The interesting point is that they distinguish between positive and negative preferences and subtract the similarity of negative preferences from positive ones.
+Therefore the results are most similar to global positive preferences and most dissimilar to global negative preferences.
+
+\subsection{University of Delaware \cite{Delaware}}
+The similarity calculation in the paper is very similar to \cite{IRIT}.
+The main difference is that it uses average of similarity for negative and positive preferences.
+Time factor is not considered in rating.
+After rating the final results are filtered based on time.

### 2013-09-19 Reports/Report1/appendixA.tex
writing draft of report 1

\section{Appendix A - Feedback data samples}
\begin{center}
\begin{longtable}{|l|l|l|l|l| p{4cm} |}
\caption[Feedback data sample]{Feedback data sample.} \\

\hline 
\multicolumn{1}{|c|}{\textbf{Corrector}} & 
\multicolumn{1}{c|}{\textbf{Translator}} & 
\multicolumn{1}{c|}{\textbf{Language}} & 
\multicolumn{1}{c|}{\textbf{Category}} & 
\multicolumn{1}{c|}{\textbf{Rating}} & 
\multicolumn{1}{p{4cm}|}{\textbf{Comment}} \\ \hline 
\endfirsthead

\multicolumn{6}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{|c|}{\textbf{Corrector}} & 
\multicolumn{1}{c|}{\textbf{Translator}} & 
\multicolumn{1}{c|}{\textbf{Language}} & 
\multicolumn{1}{c|}{\textbf{Category}} & 
\multicolumn{1}{c|}{\textbf{Rating}} & 
\multicolumn{1}{c|}{\textbf{Comment}} \\ \hline 
\endhead

\hline \multicolumn{6}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot

Bettina&Sabine&fr->de-DE&Content&5&\\ \hline
Bettina&Sabine&fr->de-DE&Formatierung&5&\\ \hline
Bettina&Sabine&fr->de-DE&Level of language&3&Korrekturen siehe Änderungen in doc-Datei, die sich hier leider über "upload a file" nicht hochladen lässt, sondern ausnahmsweise per E-mail folgt.\\ \hline
Brigitte&Jakarta&de-DE->jv&Grammar&5&\\ \hline
Brigitte&Jakarta&de-DE->jv&Formatierung&4&\\ \hline
Brigitte&Jakarta&de-DE->jv&Completeness&5&\\ \hline
Brigitte&Jakarta&de-DE->jv&Style&5&\\ \hline
Brigitte&Jakarta&de-DE->jv&Content&3&\\ \hline
Brigitte&Jakarta&de-DE->jv&Level of language&3&\\ \hline
Brigitte&Jakarta&de-DE->jv&Spelling&5&\\ \hline
Brigitte&Jakarta&de-DE->jv&Accuracy&5&\\ \hline
Brigitte&Yogyakarta&de-DE->jv&Accuracy&5&\\ \hline
Brigitte&Yogyakarta&de-DE->jv&Completeness&5&\\ \hline
Brigitte&Yogyakarta&de-DE->jv&Style&5&\\ \hline
Brigitte&Yogyakarta&de-DE->jv&Grammar&5&\\ \hline
Brigitte&Yogyakarta&de-DE->jv&Spelling&5&\\ \hline
Heinz&Olga&de-DE->ru&Formatierung&4&Die Eigennamen (lateinische Buchstaben - z.B. nativy) sind in einer vom sonstigen russischen Text abweichenden Schriftart wiedergegeben - das fällt leider auf.\\ \hline
Heinz&Olga&de-DE->ru&Level of language&5&Sehr gutes Russisch!\\ \hline
Heinz&Olga&de-DE->ru&Content&3&Einige Wörter wurden nicht ganz korrekt übertragen (statt "Auftrag" - "Projekt"); eine wesentliche Wortgruppe wurde weggelassen (beim Rabatt: "für 4 Monate").
Die Präzision der Übertragung lässt an einigen Stellen zu wünschen übrig.\\ \hline
Jakarta&Yogyakarta&de-DE->jv&Style&4&\\ \hline
Jakarta&Yogyakarta&de-DE->jv&Accuracy&4&\\ \hline
Jakarta&Yogyakarta&de-DE->jv&Completeness&4&\\ \hline
Jakarta&Yogyakarta&de-DE->jv&Spelling&4&\\ \hline
Jakarta&Yogyakarta&de-DE->jv&Grammar&4&\\ \hline
Sonja&Nicole&de-DE->en&Content&0&\\ \hline
Sonja&Nicole&de-DE->en&Level of language&0&\\ \hline
Sonja&Nicole&de-DE->en&Formatierung&0&\\ \hline
Sonja&Sabine&de-DE->en&Level of language&0& \\ \hline
Sonja&Sabine&de-DE->en&Content&0&\\ \hline
Sonja&Sabine&de-DE->en&Formatierung&0&\\ \hline
Yogyakarta&Brigitte&de-DE->jv&Completeness&5&\\ \hline
Yogyakarta&Brigitte&de-DE->jv&Accuracy&5&\\ \hline
Yogyakarta&Brigitte&de-DE->jv&Style&5&\\ \hline
Yogyakarta&Brigitte&de-DE->jv&Spelling&5&\\ \hline
Yogyakarta&Brigitte&de-DE->jv&Grammar&5&\\ \hline
Yogyakarta&Semarang&de-DE->jv&Level of language&2&\\ \hline
Yogyakarta&Semarang&de-DE->jv&Formatierung&2&\\ \hline
Yogyakarta&Semarang&de-DE->jv&Content&3&\\
\end{longtable}
\end{center}

### 2013-09-19 Reports/Report1/data.tex
writing draft of report 1

\section{Feedback Data}
After every translation, a pre-selected corrector revises the translation. After reviewing, the corrector assesses the translation and leave a feedback on it. This feedback consists of a comment and number which evaluate the quality of translation from one to five (five is the best). These feedbacks are also categorized in different aspects of translation like content, grammar, style, accuracy and etc. For each translation, the value related to each criterion (price, time, text matching and cooperation) can be fetched from database.

Since the website is working from 2011, there are about 2000 feedback records in database which related to different translators and language pairs.

Some sample records of database are shown in Appendix A.

### 2013-09-19 Reports/Report1/idea.tex
writing draft of report 1

\section{Ideas and Brainstorming}
Using data represented in Appendix A for every translation, a vector can be created that shows the relation between four criteria (time, price, text matching and cooperation) and final feedback. My idea for translators ranking consisted of two elements which both are based on the defined vector. It is formulated as follows where $R_T$ ,$H_T$ and $P_T$ denote ranking value of translator, first element (Harmonic) and second element (Privilege). $\alpha$ is the tuning factor and can be between 0 and 1.

\begin{center}
$R_T = \alpha H_T + (1-\alpha)P_T$ \\
\end{center}

The first element ($H_T$) which can be called Harmonic element shows how similar the vector is to well-ranked results and how far it is from bad-ranked results. The similarity is calculated by cosine measure. In the following formula $O_T$ denotes translator's offer and $F_i$ stands for vector of feedback. For each feedback, the feedback rate is shown in $r_i$. The formula is depicted as follows:

\begin{center}
$H_T = \sum_{i=0}^{number of feedbacks} r_i SIM(O_T, F_i)$ \\
\end{center}

The second element ($P_T$) which can be called Privilege element shows how good the offered criterion in comparison to a standard value is. In order to find the value, we need a Standard Vector ($S$) which can be achieved by calculating the average of all offered values by translators in every criterion. Here is the formulas for calculating $S$ and $G_T$. $O_{T,c}$ stands for offer value by a translator for a specific criterion. The function $f$ is used for normalizing the value. Finally $n$ denotes number of offers by translators

\begin{center}
$S = \sum_{i=0}^{n} \frac{O_{T,c}}{n}$ \\
\end{center}

\begin{center}
$G_T = \sum_{c=0}^{number of criteria} \frac{f(O_{T,c})}{S_c} $ \\
\end{center}

I suggest using $\log _2 \left( x \right)$ as function $f$. The reason for selecting base two is decreasing radically the effect of division when offer is more than two times bigger than standard value. The suggested function is depicted in Figure ~\ref{fig:FUNC} :

\begin{figure}
  \centering
    \includegraphics[width=12cm]{diagram.jpg}
  \caption{Suggested function for normalizing the criteria.}
  \label{fig:FUNC}
\end{figure}

### 2013-09-19 Reports/Report1/data.tex
revise report1

@@
-\section{Feedback Data}
-After every translation, a pre-selected corrector revises the translation.
-After reviewing, the corrector assesses the translation and leave a feedback on it.
-This feedback consists of a comment and number which evaluate the quality of translation from one to five (five is the best).
+\section{Translation Feedback Data}
+After every translation, a pre-selected corrector revises the translation and assesses the translation quality.
+Then the corrector leaves a feedback on it which consists of a comment and a number from one to five (five is the best) which evaluate the quality of translation.
 These feedbacks are also categorized in different aspects of translation like content, grammar, style, accuracy and etc.
-For each translation, the value related to each criterion (price, time, text matching and cooperation) can be fetched from database.
+For each translation, criterion values (price, time, text matching and cooperation) offered by translator can be fetched from database.
 
-Since the website is working from 2011, there are about 2000 feedback records in database which related to different translators and language pairs.
+Since the website is working from 2011, there are about 2000 feedbacks in database. These records contain the assessment of different translators and language pairs in different criterion categories.
 

### 2013-09-19 Reports/Report1/idea.tex
revise report1

@@
 \section{Ideas and Brainstorming}
-Using data represented in Appendix A for every translation, a vector can be created that shows the relation between four criteria (time, price, text matching and cooperation) and final feedback.
+Using data represented in Appendix A for every translation, a vector can be created that shows the relation between four criteria (time, price, text matching and cooperation) and final feedbacks.
 My idea for translators ranking consisted of two elements which both are based on the defined vector.
@@
 
-The first element ($H_T$) which can be called Harmonic element shows how similar the vector is to well-ranked results and how far it is from bad-ranked results.
+The first element ($H_T$) which can be called Harmonic element shows how similar the vector is to high-ranked results and how far it is from low-ranked results.
 The similarity is calculated by cosine measure.
-In the following formula $O_T$ denotes translator's offer and $F_i$ stands for vector of feedback.
-For each feedback, the feedback rate is shown in $r_i$.
+In the following formula $O_T$ denotes translator's offer and $F_i$ stands for vector of feedback and $r_i$ shows the feedback's rate.
 The formula is depicted as follows:
@@
 
-The second element ($P_T$) which can be called Privilege element shows how good the offered criterion in comparison to a standard value is.
+The second element ($P_T$) which can be called Privilege element shows how good the offered criteria are in comparison to a standard value.
 In order to find the value, we need a Standard Vector ($S$) which can be achieved by calculating the average of all offered values by translators in every criterion.
 Here is the formulas for calculating $S$ and $G_T$.
-$O_{T,c}$ stands for offer value by a translator for a specific criterion.
+$O_{T,c}$ stands for offered value by a translator for a specific criterion.
 The function $f$ is used for normalizing the value.
-Finally $n$ denotes number of offers by translators
+Finally $n$ denotes number of translators' offers.
 
 \begin{center}
-$S = \sum_{i=0}^{n} \frac{O_{T,c}}{n}$ \\
+$S_c = \sum_{i=0}^{n} \frac{O_{T,c}}{n}$ \\
 \end{center}
@@
 \begin{center}
-$G_T = \sum_{c=0}^{number of criteria} \frac{f(O_{T,c})}{S_c} $ \\
+$G_T = \sum_{c=0}^{number of criteria} f(\frac{O_{T,c}}{S_c}) $ \\
 \end{center}
 
-I suggest using $\log _2 \left( x \right)$ as function $f$.
+I suggest using $f = \log _2 \left( x \right)$.
 The reason for selecting base two is decreasing radically the effect of division when offer is more than two times bigger than standard value.
-The suggested function is depicted in Figure ~\ref{fig:FUNC} :
+The suggested function is depicted in Figure ~\ref{fig:FUNC}.
 

### 2013-10-28 Paper/introduction.tex
first darft of paper

*** TODO: Introduction to expert retrieval and learn to rank goes here ***

The designed framework can be categorized in domain of on-line translation. The framework aims to find the best translator-corrector combination for a client who seeks for a reasonable offer to translate a document.

The profile of every translator consists of different aspects like offered price per word, translation time per word, experience and quality of translation in a specific language pair (source and destination languages). Based on client's document, the system figures out the value of each aspect and offers the first three most related translators. As it is clear, the aspects are in different scales (price in currency, time in minute and etc.). It should also mentioned that the one with best offer in all aspects (lowest price, fastest time, most similar to previous experience and etc.) may not be the best offer and leads to a low quality translation and unsatisfied client.

In order to evaluate the quality of translators and also whole the task, a feedback system for corrector and client is considered. After finishing translator's task, the corrector starts revising the text and leaving a feedback on it. The feedback of corrector which is a number between one to five is used as a base for estimating the proficiency of translator. Then by delivering the task to the client, his feedback is asked. The feedback of client is used to deploy and leverage ranking system.

In Section II, the designed Translator-Expert Retrieval framework is discussed in detail. Then, Section III summarizes system evolution and achieved results. Finally conclusion is written down in section IV.

### 2013-10-28 Paper/ranking.tex
first darft of paper

In this section, first the framework's elements is denoted. Then the techniques for calculating documents similarity and some restrictions are described. At the end, the strategy for ranking and choosing the best possible translator is discussed.

\subsection{Framework Denotation}
As it is depicted in the following formula ,the profile of each translator related to the query (
$\overrightarrow{T_{i,q}}$) is a vector where $i$ is the iterator for translators and $q$ is the corresponding query. In the formula, $t_q$ and $c_q$ stand for estimated time and cost for translation. $e_q$ denotes the experience or knowledge of translator which is calculated based on similarity between query document and all previous-translated documents. The technique applied for calculating $e_q$ is explained further. $s$ shows the quality of translator and how previous tasks have been estimated. It is achieved by calculating the average value of correctors' feedbacks. The value is between one (very bad) to five (perfect).

\begin{center}
$\overrightarrow{T_{i,q}} = \{ t_{i,q}, c_{i,q}, e_{i,q}, s_i \}$ \\
\end{center}

After finishing the task and gathering feedbacks of clients, based on the offered values for each translation, feedback vectors can be built up. In the following formula $j$ denotes the iteration for feedbacks and $f_j$ stands for feedback value.

\begin{center}
$\overrightarrow{F_j} = \{ t_j, c_j, e_j, s_j, f_j \}$ \\
\end{center}

\subsection{Documents Similarity}
In order to calculate $e_q$, we need to figure out the similarity between query document and all previous-translated documents. The similarity is calculated by Lucene library and is denoted as $SIM$ function. Every pre-translated document is assessed by corrector's feedback ($f'$). In additional to these documents, every translator may submit some other documents which had been translated before and clearly not assessed. In the framework, we assume their quality as medium (two). In the following formula $d_iterator$ and $d_q$ stand for pre-translated and query documents. $n$ and $m$ are the number of pre-translated document inside and outside the framework.

\begin{center}
$e_{i,q} = \sum_{0<k<n} f'_k SIM(d_k, d_q) + \sum_{0<l<m} 2 SIM(d_l, d_q) $ \\
\end{center}

***TODO: The Lucene's similarity value does not have a special range and is a number greater than or equal to zero. Here there can be some discussions about the meaning of the achieved value or probable alternative solutions ***

\subsection{Ranking}
***TODO: Ranking method goes here***

### 2013-10-30 Paper/casestudy.tex
writing case study

The designed framework can be categorized in domain of on-line translation. It aims to find the best translator-corrector pair for a client who seeks for a reasonable offer to translate a document.

Every expert creates a profile by registering in the framework. The expert can play the role of translator or corrector. The profile consists of offered price per word for translation/correction, translation/correction time per word, experience in a special context and proficiency in a specific language pair (source and destination languages). Based on client's document, the system figures out the value of each aspect and offers the first three most related translator-corrector pairs.

In order to evaluate the proficiency of experts, an evaluation system based on feedbacks of correctors, clients and evaluators is provided. After finishing translator's task, the corrector starts revising the text as well as assessing translation quality. The feedback of corrector which is a number between one to five is used for estimation the proficiency of translator. Then by delivering the translation, client's feedback is asked. The feedback of client is used to deploy and leverage ranking system. Apparently, an evaluation team consisted of business experts are consistently evaluating the quality of ranking system.

In the rest of the section, we denote the framework's elements. As it is depicted in the following formula ,the profile of each expert related to the query is a vector where $q$ is the corresponding query. In the formula, $t_q$ and $c_q$ stand for estimated time and cost proposed by the expert. The prefix $T$ and $C$ stand for role of expert as translator or corrector. $s_q$ denotes the experience or knowledge of expert in a special context which is calculated based on similarity between query document and all previous-translated documents. The technique applied for calculating $s_q$ is explained further. $p$ shows the proficiency of expert and how previous tasks have been estimated by other experts. It is being achieved by calculating the average value of correctors' feedbacks. The value is between one (very bad) to five (perfect).

\begin{center}
$\overrightarrow{Profile_{q}} = \{ t_{T,q}, t_{C,q}, c_{T,q}, c_{C,q}, s_q, p \}$ \\
\end{center}

***Question: How should we handle the underlying relation between $s_q$ and $p$?***

The evaluation results are also denoted as follows. In the following formula $e$ stands for evaluation value which can be between one (very bad) and five (perfect). Because of some practical considerations, delivery time $t$ is used in evaluation process (not separated schedule time of translator and corrector).

\begin{center}
$\overrightarrow{Evaluation_{q}} = \{ t, c_{T,q}, c_{C,q}, s_{T,q}, s_{C,q}, p_T, p_C, e \}$ \\
\end{center}

### 2013-10-30 Paper/introduction.tex
writing case study

@@
-*** TODO: Introduction to expert retrieval and learn to rank goes here ***
+*** TODO: Introduction ***
 
-The designed framework can be categorized in domain of on-line translation.
-The framework aims to find the best translator-corrector combination for a client who seeks for a reasonable offer to translate a document.
+% The designed framework can be categorized in domain of on-line translation.
+The framework aims to find the best translator-corrector % combination for a client who seeks for a reasonable offer to translate a document.
 
-The profile of every translator consists of different aspects like offered price per word, translation time per word, experience and quality of translation in a specific language pair (source and destination languages).
+% The profile of every translator consists of different aspects like offered price per word, translation time per word, experience and  quality of translation in a specific language pair (source and destination languages).
 Based on client's document, the system figures out the value of each aspect and offers the first three most related translators.
 As it is clear, the aspects are in different scales (price in currency, time in minute and etc.).
-It should also mentioned that the one with best offer in all aspects (lowest price, fastest time, most similar to previous experience and etc.) may not be the best offer and leads to a low quality translation and unsatisfied client.
+It should also mentioned that the one with best offer in all aspects (lowest price, fastest time, most %similar to previous experience and etc.) may not be the best offer and leads to a low quality translation and unsatisfied client.
 
-In order to evaluate the quality of translators and also whole the task, a feedback system for corrector and client is considered.
+% In order to evaluate the quality of translators and also whole the task, a feedback system for corrector and client is considered.
 After finishing translator's task, the corrector starts revising the text and leaving a feedback on it.
@@
 
-In Section II, the designed Translator-Expert Retrieval framework is discussed in detail.
+% In Section II, the designed Translator-Expert Retrieval framework is discussed in detail.
 Then, Section III summarizes system evolution and achieved results.

### 2013-12-24 docs/old/problem.tex
adding new files

\section{Problem Statement}
\subsection{Introduction}
The problem can be defined in domain of on-line translation. Systems in this domain aim to establish a reasonable connection between clients who ask for translation and translators.

In the following paragraph, first the whole scenario and the problem which is tackled in the paper is described. Then, some specific required characteristics of hypothetical system for solving the problem are mentioned.

\subsection{Scenario}
The client uploads documents to the website and asks for translators in different languages. Based on five criteria, the system starts searching for the best three translators. These criteria are cost, delivery time, frequent cooperation, similarity to previous translations and quality of the translator. Every criterion has also its weight which defines the importance from client's point of view.

Cost, delivery time, frequent cooperation and quality are calculated using existing information in system's database like the schedule of translator, proposed price for each language pair, assessment of administrator of the quality of translation and etc.. Finding the value related to the similarity to previous translations criterion is more complex. In primitive stages of translator's registration and assessment, every translator uploads the documents which she has translated before. In addition, during the cooperation of translator with the company, some other translated documents are gathered in the system. These information should be used to find the best translators for the submitted document. The more relevant previous tasks to current text, the higher value for similarity criterion.

After merging the results of different criteria, the system represents the most appropriate translators to the client.

Following finishing translation task, a qualified proof-reader chose by client reads the translation through and sends some feedbacks or corrections to translator. At the end the proof-reader rates the whole task done by translator. After delivering the translation, user leaves a feedback on the translation.

Design and implement a system for calculating the similarity value as well as an algorithm for retrieving experts (translators) is the aim of the current study.

\subsection{Specifications}
Some specific characteristics should be mentioned for the project:

\begin{itemize}
\item Short response time.
\item Different languages.
\item While the files are in different formats, the content is retrieved and prepared as plain text in Unicode format.
\end{itemize}

### 2013-12-24 docs/reports/report1/reviewedpapers.tex
adding new files

--- 2013-09-17 Reports/Report1/reviewedpapers.tex
@@
-\section{Overview On Reviewed Papers}
-Since the defined problem in 2012 TREC Contextual Suggestion Track is some how similar to the current problem, I focused on reviewing the solution proposed by participants of this Track.
-In TREC Contextual Suggestion Track, different factors like personal preferences, location and time influence on ranking of venues.
+\section{Reviewed Papers}
+Since the defined problem in 2012 TREC - Contextual Suggestion Track is some how similar to the current problem, I focused on reviewing the solution proposed by participants of this Track.
+In Contextual Suggestion Track, different factors like personal preferences, location and time influence on ranking of venues.
 I have tried to concentrate on the way different papers have encountered with the ranking problem in order to gain some ideas for current problem.
@@
 \subsection{IRIT \cite{IRIT}}
-I found the paper quite interesting as it acquired the first ranking between other participants.
+I found the paper quite interesting as it also acquired the first ranking between other participants.
 Like some other papers, they also create a Vector Space Model and calculate similarity based on cosine measure.

### 2013-12-24 docs/seminar/evaluation.tex
adding new files

***Question: Is it necessary to consider just a specific language pair? Or ML can be applied on whole the data.***

***Question: Based on discussion, there are current formulas:
\begin{center}
$SCORE_{T,q} = \{ c_{T,q}, s_{T,q}, p \}$ \\
\end{center}
\begin{center}
$SCORE_{C,q} = \{ c_{C,q}, s_{C,q}, p \}$ \\
\end{center}
\begin{center}
$SCORE_{q} = \alpha.SCORE_{T,q} + \beta.SCORE_{C,q}$ \\
\end{center}
\begin{center}
$RANK_{q} = \{ t_q, e _q, SCORE_q \}$ \\
\end{center}

How can we achieve $SCORE_{T,q}$ and $SCORE_{C,q}$?
***

***TODO: Evaluation ***

### 2013-12-24 docs/seminar/methods.tex
adding new files

The subjects which are studied during design of the framework can be classified into two main topics. First aggregating results of similarity between query document and previous translated documents in order to estimate expert's proficiency. Second applying a learning to rank method to find and offer the best experts.

\subsection{Aggregation Functions}
In order to calculate experience of expert related to client's document, we need to figure out the similarity between query document and all previous-translated documents.

***TODO: Introducing aggregation methods and choosing one for the framework ***
%The similarity is calculated by Lucene library and is denoted as $SIM$ function. Every pre-translated document is assessed by corrector's feedback ($f'$). In additional to these documents, every translator may submit some other documents which had been translated before and clearly not assessed. In the framework, we assume their quality as medium (two). In the following formula $d_iterator$ and $d_q$ stand for pre-translated and query documents. $n$ and $m$ are the number of pre-translated document inside and outside the framework.

\subsection{Learning To Rank}
***TODO: Ranking methods goes here. Comparing between Point-wise, Pair-wise and List-wise and choosing the most related one for the framework ***

### 2013-12-24 docs/reports/finalreport/report.tex
starting project final report

\input{config}
\input{title}

\begin{document}

\maketitle
\begin{abstract}
We did experiments on three datasets of different size and with different characteristics using Regression Algorithms. Four different algorithms where used for the experiment and for this four we did experiments varying their arguments data scaling and imputation techniques for missing data. In the report we first give an overview over the algorithms used, then we interpret the results of our experiments for each dataset and do a comparison of the different algorithms. In the end we try to compare the results of all datasets and draw conclusions.
\end{abstract}

\vfill
\tableofcontents
\newpage

\input{introduction}
\newpage
\input{problem}
\newpage
\input{architecture}
\newpage
\input{design}
\newpage
\input{development}
\newpage
\input{future}
\newpage

\bibliographystyle{plain}
\bibliography{report}

\end{document}

### 2013-12-25 docs/reports/finalreport/architecture.tex
finishing final report

\section{System Architecture and Design}
The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture. As it is depicted in Figure \ref{fig:architecture}, the system is consisted of three main layers : Interface, Business and Data Access Layer. Data is passed between the layers using Model objects.

Interface layer can be divided into two main parts. Server side and client side. Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. It's main purpose is mapping Model View objects of Interface Layer to Model objects and passing them to Business Layer and vice verse. Client side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for applying the model are explained in the next section.

Using AOP (Aspect-Oriented Programming), logging, error handling and security system are designed on top of other layers.

As well as mentioned architectural patterns, following design patterns are used:
\begin{itemize}
	\item Dependency Injection and Inversion of Control implemented in Interface Layer
	\item Singleton Repository in Data Access Layer
	\item Unit of Work for handling transactions
\end{itemize}

\begin{figure}[h]
\begin{center}
\includegraphics[scale=0.9]{figures/architecture.jpg}
\caption{System Architecture
\label{fig:architecture}}
\end{center}
\end{figure}

### 2013-12-25 docs/reports/finalreport/design.tex
finishing final report

\section{Tools and Technologies}
In this section, the main applied tools, technologies and libraries are briefly described following by their usage in the system.

\begin{itemize}
	\item \textbf{C\texttt{\#}.NET 4.5:} As the main programming language, the project is developing on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
	\item \textbf{ASP.NET 4.5:} It provides the required framework for web programming. MVC.NET is used as the main server side platform.
	\item \textbf{MS SQL Azure:} As the system is deployed on Windows Azure platform, SQL Azure is selected as relational database.
	\item \textbf{Windows Azure:} Some special services like Cache, Storage and Service Bus are widely used in the project.
	\item \textbf{Lucene.NET:} The core of text processing, indexing and search is handled by Lucene. Lucene.NET is implemented by line to line translating from its Java version. While Lucene in Java provides more options, the .NET version is used to keep the integrity of project.
	\item \textbf{LINQToSQL:} Regarding to high integrity of the tool with MS SQL Server, it is used as ORM (Object-Relational Mapping).
	\item \textbf{HunAlign\cite{hunalign}:} It is light library which aligns bilingual text on the sentence level. Its input is tokenized and sentence-segmented text in two languages. In the simplest case, its output is a sequence of bilingual sentence pairs (bisentences). In the presence of a dictionary, hunalign uses it, combining this information  with Gale-Church sentence-length information. In the absence of a dictionary, it first falls back to sentence-length information, and then builds an automatic dictionary based on this alignment. Then it realigns the text in a second pass, using the automatic dictionary. The library is used for developing the translation memory in sentence level based on original and translated text.
	\item \textbf{KnockoutJS:} A JQuery-based library for applying MVVM pattern and associating between DOM and data model.
	\item \textbf{BreezeJS:} A handy JQuery-based library for declaring object models on client side and executing HTML Verbs integrated with ASP.NET MVC.
	\item \textbf{AutoMapper:} Widely used for mapping objects specially from object Models to object View Models.
	\item \textbf{AutoFac:} It is an IoC container for Microsoft .NET which manages the dependencies between classes.
	\item \textbf{SignalR:} It is a library for ASP.NET that makes it simple to add real-time web functionality. Using the library, we can easily have server-side code push content to the connected clients as it happens, in real-time. Chat and notification systems are developed using this library.
	\item \textbf{Postsharp:} It is an AOP framework for .NET. Most AOP implementation is based on the library.
\end{itemize}

### 2013-12-25 docs/reports/finalreport/development.tex
finishing final report

\section{System Development}
In this section, some special points related to development of different components are described.

\subsection{Order}
Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. Complex business of the company for applying query, offering translators and purchasing order urges using design models and standards.
\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translator's ranking, a data accumulating system is designed. Similar to Order, based on query document it offers three translators and stores client's choice. The data gathered by the system is used in a Machine Learning program using Learning to Rank algorithms in order to discover the underlying pattern for proposing the translators. The details of the project is described in Seminar lecture related to the project. In contrast to Order system, it eliminates translator's picture and name. It prevents bias in final answer by client (estimator) and puts emphasis on presented criteria.
\subsection{Text Matching}
Using Lucene translator's documents are stored based on their language. In order to achieve the final text matching value, the similarity between each document and query document is calculated. The problem here is the aggregation algorithm between the results. Finally, based on the results that are reported in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
\subsection{Translation Memory}
As it's mentioned before, the aim of Translation Memory system is helping the translators to have an access to their previous-translated texts and applying them to their new translations. HunAlign is used to align the sentences of one text with the sentences of its corresponding text in another language. Although the library tends to be very error-prone specially for complex texts, adding dictionary and using rather simple texts lead to more reasonable results. At the end, Lucene is used for indexing and searching the sentences.

### 2013-12-25 docs/reports/finalreport/introduction.tex
finishing final report

\section{Introduction}
As a hub for professional translation services, Nativy \cite{nativy}(founded 2011 in Vienna) offers its customers top-quality translations at reasonable terms.

The company works exclusively with qualified translators into their native language. All Nativy translations are reviewed in accordance with EN 15038, the European Quality Standard for Translation Services, and translators have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.

By providing the platform, regardless to geographical location of translators and clients, they can communicate and proceed the translation process. It eases translating text to even not-so-popular languages and also reduces the final cost.

The features regarding to the internship has been developed since Summer 2013.

In the following, first we address the problem. Then in system architecture as well as design patterns and development techniques are explained. At the end related work to the project is briefly met.

### 2013-12-25 docs/reports/finalreport/problem.tex
finishing final report

\section{Problem Statement}
The client uploads documents to the website and asks for translators in different languages. Based on four criteria, the system starts searching for the best three translators. These criteria are cost, delivery time, frequent cooperation and text matching. Every criterion has also its weight which defines the importance from client’s point of view.

Each translator is proposing a price for each language pair which is used for calculating final cost. Delivery time is calculated based on the schedule of translator. Finally, in order to find text matching value, the similarity between query document and previous translated documents is aggregated. In primitive steps of registration, every translator uploads the documents has been translated before. These documents are also considered for calculating the similarity.

After merging the results of different criteria, the system represents the most appropriate translators to the client. By choosing the translator and following payment process, the translation starts. After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator. At the end the proof-reader rates the translation from different aspects.

The problems and requirements addressed in the project are as follows:
\begin{itemize}
	\item wizard-like page for ordering process in a SPA (Single Page Application) structure.
	\item Indexing previous-translated texts and finding an aggregation function for their similarity values with query document.
	\item Finding and tuning a ranking function for finding the best three translators among all.
	\item Calculating delivery time based on translator's schedule.
	\item Web API interface as well as web interface
	\item Payment process.
	\item Short response time.
	\item Considering different languages and timezones.
\end{itemize}

### 2013-12-25 docs/reports/finalreport/report.tex
finishing final report

@@
 \begin{abstract}
-We did experiments on three datasets of different size and with different characteristics using Regression Algorithms.
-Four different algorithms where used for the experiment and for this four we did experiments varying their arguments data scaling and imputation techniques for missing data.
-In the report we first give an overview over the algorithms used, then we interpret the results of our experiments for each dataset and do a comparison of the different algorithms.
-In the end we try to compare the results of all datasets and draw conclusions.
+The reports explains the efforts done by design and develop a translator
+retrieval system.
+The system can be defined in domain of on-line translation.
+It aims to find an appropriate translator for a client and manages the process till the last step.
+Besides, by providing a translation memory system translators can apply their previous translated texts in their new ones.
+In the project, C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used.
+It is designed based on DDD (Data Driven Design) model.
+Windows Azure is also selected as deployment environment.
 \end{abstract}
@@
 \newpage
-\input{future}
-\newpage
 

### 2013-12-27 docs/seminar/introduction.tex
writing introduction

The goal of expertise retrieval is to link humans to expertise areas, and vice versa. In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er} \cite{er-community-aware}.

The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects.

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}. Expertise retrieval has received increasing interest since the introduction of an expert finding task in the Text Retrieval Conference (TREC) 2005 \cite{trec2005} \cite{er-community-aware}.

Two principal approaches are proposed in \cite{trec2005} based on probabilistic language modeling techniques. They were formalized as so-called candidate models and document models. the candidate-based approach is also referred to as
profile-based method in builds a textual representation of candidate experts and then rank them based on the query. The document models' idea is to first find documents that are relevant to the topic and then locate the experts associated with these documents \cite{er}.

Ranking techniques are mostly one of the essential parts of IR frameworks. In recent years, Learning to Rank (L2R) has been studied extensively specially for document retrieval. It refers to machine learning techniques for training the model in a ranking task \cite{er}. In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \cite{l2r-intro}.

As well as ranking techniques, aggregation functions have a solid effect on the performance of IR systems. Aggregate tasks are those where documents' similarities are not
the final outcome, but instead an intermediary component. In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.

This paper addresses the problem of searching translators as expertises. We have applied Learning to Rank in a candidate-based approach. Besides, different aggregation algorithms related to documents of translators has been studied.

The remaining of the paper is organized as follows. In Section \ref{sec:casestudy}, the Translator-Expert Retrieval framework is described in detail. Then, Section \ref{sec:methods} explains methods used in the study. In Section \ref{sec:apply}, we report the result of applied methods on the framework. Finally, we conclude the study in Section \ref{sec:conclusion}.

### 2013-12-28 docs/seminar/casestudy.tex
writing case study

\section{Case Study}
\label{sec:casestudy}
The data flow of expert searching is depicted in Figure\ref{fig:architecture}. The client submits a document and searches translators of a specific target language. Based on query document, the framework figures out offered price, delivery time, proficiency and number of cooperation times related to each translator. The result is processing by a ranking system and the most related translators are offered to the client.

As it is shown in Figure\ref{fig:architecture}, the essential components of the framework are \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiler}.

\begin{figure*}[h]
\begin{center}
\includegraphics[scale=0.8]{figures/dataflow.jpg}
\caption{System Data Flow
\label{fig:architecture}}
\end{center}
\end{figure*}

\textit{Ranking} system uses L2R to return the most related translators to the query. The training data is provided by a group of evaluators who are familiar with business of company. In an evaluation system, they choose a translator between three offered ones. In order to prevent bias in evaluation, the translators are offered randomly and without name and picture. Applied method and results are described in Section \ref{sec:apply}. \textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library. The similarity between query and indexed documents is used as a base for estimation of translator's proficiency. In the next step, calculated similarities are aggregated. The applied aggregation function is described in Section \ref{sec:apply}. \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds a special data structure to outperform the response time. The detail of the process is out of scope of the paper .At last, \textit{Profiler} accumulates personal information of translators, their preferences as well as offered price and translation duration per word.

Beside translator, a proofreader selected by the client is revising the final translation. The proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language) as well. The assessment is defined as a value between one (very bad) to five (perfect). As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translation proficiency.

### 2013-12-28 docs/seminar/methods.tex
writing case study
writing methods-aggregation function

@@
-The subjects which are studied during design of the framework can be classified into two main topics.
-First aggregating results of similarity between query document and previous translated documents in order to estimate expert's proficiency.
-Second applying a learning to rank method to find and offer the best experts.
+\section{Methods}
+\label{sec:methods}
+In this section, we study thoroughly different methods and algorithms regarding to Aggregation Functions and Learning to Rank.
+The study will shed light on the problem of picking the most appropriate algorithm regarding to the project.
 
 \subsection{Aggregation Functions}
-In order to calculate experience of expert related to client's document, we need to figure out the similarity between query document and all previous-translated documents.
+As a usual scenario in expert retrieval systems, first each document related to an expert is scored and ranked regarding to query.
+Then, the top $N$ document scores associated with a candidate expert are aggregated in order to rank the experts.
+The aggregation function has a big impact on the performance of Expert Retrieval system.
 
-***TODO: Introducing aggregation methods and choosing one for the framework ***
-%The similarity is calculated by Lucene library and is denoted as $SIM$ function.
-Every pre-translated document is assessed by corrector's feedback ($f'$).
-In additional to these documents, every translator may submit some other documents which had been translated before and clearly not assessed.
-In the framework, we assume their quality as medium (two).
-In the following formula $d_iterator$ and $d_q$ stand for pre-translated and query documents.
-$n$ and $m$ are the number of pre-translated document inside and outside the framework.
+The effect of different features on aggregation function is is studied in \cite{agg-gp2}.
+As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$.
+Comparing query-based features using statistical measures, it inferred that the features may not, in general, be able to predict the optimal number of documents to aggregate for each query.
+Individual Expert Features is discussed in the next step.
+It is shown that relevant experts are associated with a higher ranked document than non-relevant experts.
+More interestingly, relevant experts are associated with less documents on average.
+
+Macdonald et al.\cite{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise.
+Eleven data fusion as well as three statistically different document weighting were tested.
+In practice, the approach considers both number of documents and expert features regarding to the ranking score of the documents.
+The results show that while some of adapted voting techniques are most likely outperform others, the proposed approach is effective when using appropriate one.
+
+Later on, focusing on related features discussed before Cummins et al.\cite{agg-gp2} comes up with a novel idea.
+It uses genetic programming to learn a formula for the weights of document associations within the candidate profiles.
+The formula denoted as $GP2$ is as follows:
+
+$GP2 = \frac{\sqrt{\sqrt{2/{no\_docs_x}_i}}/(\sqrt{(10/R)+R}}{\sqrt{sq(10/R)+R+sq(10/R)+\sqrt{R*2}}}$
+
+where $R$ is the rank of the document in the initial ranking and ${no\_docs_x}_i$ is the total number of documents associated with expert $x_i$.
 
 \subsection{Learning To Rank}
-***TODO: Ranking methods goes here. Comparing between Point-wise, Pair-wise and List-wise and choosing the most related one for the framework ***
+TODO

### 2013-12-28 docs/seminar/evaluation.tex
writing case study
writing methods-aggregation function
starting apply methods section

@@
-***Question: Is it necessary to consider just a specific language pair? Or ML can be applied on whole the data.***
+\section{Apply The Methods and Results}
+\label{sec:apply}
+In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characters and data.
 
-***Question: Based on discussion, there are current formulas:
-\begin{center}
-$SCORE_{T,q} = \{ c_{T,q}, s_{T,q}, p \}$ \\
-\end{center}
-\begin{center}
-$SCORE_{C,q} = \{ c_{C,q}, s_{C,q}, p \}$ \\
-\end{center}
-\begin{center}
-$SCORE_{q} = \alpha.SCORE_{T,q} + \beta.SCORE_{C,q}$ \\
-\end{center}
-\begin{center}
-$RANK_{q} = \{ t_q, e _q, SCORE_q \}$ \\
-\end{center}
+\subsection{Aggregation Functions}
+TODO
 
-How can we achieve $SCORE_{T,q}$ and $SCORE_{C,q}$?
-***
-
-***TODO: Evaluation ***
+\subsection{Learning To Rank}
+TODO

### 2013-12-28 docs/seminar/abstract.tex
writing abstract

Expertise Retrieval, whose task is to suggest people with relevant expertise regarding to a query, has received increasing interest in recent years. In this paper, we proposed an Expert Retrieval platform narrowed down to Translators as experts. Issues and obstacles during design and development as well as acquired solutions and results are reported. Ranking the translators using Learning to Rank as well as documents' aggregation functions are two main issues which are specifically studied in the paper.

### 2013-12-28 docs/seminar/methods.tex
writing abstract

@@
 
-$GP2 = \frac{\sqrt{\sqrt{2/{no\_docs_x}_i}}/(\sqrt{(10/R)+R}}{\sqrt{sq(10/R)+R+sq(10/R)+\sqrt{R*2}}}$
+\begin{align*}
+GP2 = \frac{\sqrt{\sqrt{2/{no\_docs_x}_i}}/(\sqrt{(10/R)+R}}{\sqrt{sq(10/R)+R+sq(10/R)+\sqrt{R*2}}}
+\end{align*}
 
+\noindent 
 where $R$ is the rank of the document in the initial ranking and ${no\_docs_x}_i$ is the total number of documents associated with expert $x_i$.

### 2013-12-29 docs/reports/finalreport/architecture.tex
revising finalreport - writing apply methods of aggregation functions

@@
-\section{System Architecture and Design}
+\section{Architecture and Design}
 The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture.
@@
 Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model.
-It's main purpose is mapping Model View objects of Interface Layer to Model objects and passing them to Business Layer and vice verse.
+It's main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice verse.
 Client side web pages are designed based on MVVM (Model-View, View, Model) model.
-Tools used for applying the model are explained in the next section.
+Tools used for applying the model are explained in Section\ref{sec:tools}.
 
-Using AOP (Aspect-Oriented Programming), logging, error handling and security system are designed on top of other layers.
+Using AOP (Aspect-Oriented Programming), logging, error handling and security are designed on top of other layers.
 

### 2013-12-29 docs/reports/finalreport/design.tex
revising finalreport - writing apply methods of aggregation functions

@@
 \section{Tools and Technologies}
+\label{sec:tools}
 In this section, the main applied tools, technologies and libraries are briefly described following by their usage in the system.
@@
 \begin{itemize}
-	\item \textbf{C\texttt{\#}.NET 4.5:} As the main programming language, the project is developing on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
+	\item \textbf{C\texttt{\#}.NET 4.5:} As the main programming language, the project is being developed on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
 	\item \textbf{ASP.NET 4.5:} It provides the required framework for web programming. MVC.NET is used as the main server side platform.
@@
 While Lucene in Java provides more options, the .NET version is used to keep the integrity of project.
-	\item \textbf{LINQToSQL:} Regarding to high integrity of the tool with MS SQL Server, it is used as ORM (Object-Relational Mapping).
-	\item \textbf{HunAlign\cite{hunalign}:} It is light library which aligns bilingual text on the sentence level.
+	\item \textbf{LINQToSQL:} Regarding to high integrity of the tool with MS SQL Server, LINQToSQL is used as ORM (Object-Relational Mapping) tool.
+	\item \textbf{HunAlign\cite{hunalign}:} A light library which aligns bilingual text on the sentence level.
 Its input is tokenized and sentence-segmented text in two languages.
@@
 	\item \textbf{BreezeJS:} A handy JQuery-based library for declaring object models on client side and executing HTML Verbs integrated with ASP.NET MVC.
-	\item \textbf{AutoMapper:} Widely used for mapping objects specially from object Models to object View Models.
-	\item \textbf{AutoFac:} It is an IoC container for Microsoft .NET which manages the dependencies between classes.
-	\item \textbf{SignalR:} It is a library for ASP.NET that makes it simple to add real-time web functionality.
+	\item \textbf{AutoMapper:} Widely used for mapping objects specially from Model objects to View-Model ones.
+	\item \textbf{AutoFac:} An IoC container integrated for Microsoft .NET which manages the class dependencies.
+	\item \textbf{SignalR:} A library for ASP.NET that makes it simple to add real-time web functionality.
 Using the library, we can easily have server-side code push content to the connected clients as it happens, in real-time.
 Chat and notification systems are developed using this library.
-	\item \textbf{Postsharp:} It is an AOP framework for .NET. Most AOP implementation is based on the library.
+	\item \textbf{Postsharp:} An framework for developing AOP in .NET.
 \end{itemize}

### 2013-12-29 docs/reports/finalreport/development.tex
revising finalreport - writing apply methods of aggregation functions

@@
-\section{System Development}
-In this section, some special points related to development of different components are described.
+\section{Development}
+In this section, some special issues related to development of different components are described.
 
@@
 Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS.
-Complex business of the company for applying query, offering translators and purchasing order urges using design models and standards.
+Complex business of the company in applying query, offering translators and purchasing order urges using design models and standards.
 \subsection{Machine Learning's Data Accumulating}
@@
 Similar to Order, based on query document it offers three translators and stores client's choice.
-The data gathered by the system is used in a Machine Learning program using Learning to Rank algorithms in order to discover the underlying pattern for proposing the translators.
-The details of the project is described in Seminar lecture related to the project.
-In contrast to Order system, it eliminates translator's picture and name.
-It prevents bias in final answer by client (estimator) and puts emphasis on presented criteria.
+The data gathered by the system is used in a Machine Learning program using Learning to Rank algorithms.
+It aims to discover the underlying pattern for proposing the translators.
+The details of the project is described in seminar lecture related to the project.
+In contrast to Order system, the system eliminates translator's picture and name which prevents bias in final answer by estimator and puts emphasis on the presented criteria.
 \subsection{Text Matching}
-Using Lucene translator's documents are stored based on their language.
+Using Lucene, translator's documents are stored regarding to their languages.
 In order to achieve the final text matching value, the similarity between each document and query document is calculated.
-The problem here is the aggregation algorithm between the results.
-Finally, based on the results that are reported in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
+The main problem here is the way to  aggregate result scores.
+As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
 \subsection{Translation Memory}
-As it's mentioned before, the aim of Translation Memory system is helping the translators to have an access to their previous-translated texts and applying them to their new translations.
-HunAlign is used to align the sentences of one text with the sentences of its corresponding text in another language.
-Although the library tends to be very error-prone specially for complex texts, adding dictionary and using rather simple texts lead to more reasonable results.
-At the end, Lucene is used for indexing and searching the sentences.
+As it's mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations.
+In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in another language.
+Although the algorithm is very error-prone specially for complex texts, adding dictionary and using rather simple and straightforward texts lead to more reasonable results.
+At the end, Lucene indexes the text and provides searching abilities.

### 2013-12-29 docs/reports/finalreport/introduction.tex
revising finalreport - writing apply methods of aggregation functions

@@
 \section{Introduction}
-As a hub for professional translation services, Nativy \cite{nativy}(founded 2011 in Vienna) offers its customers top-quality translations at reasonable terms.
+As a hub for professional translation services, nativy \cite{nativy}(founded 2011 in Vienna) offers its customers top-quality translations at reasonable terms.
 
 The company works exclusively with qualified translators into their native language.
-All Nativy translations are reviewed in accordance with EN 15038, the European Quality Standard for Translation Services, and translators have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.
+All nativy translations are reviewed in accordance with EN $15038$, the European Quality Standard for Translation Services, and translators have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.
 
-By providing the platform, regardless to geographical location of translators and clients, they can communicate and proceed the translation process.
-It eases translating text to even not-so-popular languages and also reduces the final cost.
+Using the platform, regardless to geographical location of translators and clients, they can communicate and proceed a translation process.
+It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.
 
-The features regarding to the internship has been developed since Summer 2013.
-
-In the following, first we address the problem. Then in system architecture as well as design patterns and development techniques are explained. At the end related work to the project is briefly met.
+In the following, first I describe system requirements.
+Then system architecture and design are explained.
+Tools and Technologies applied in the platform are Section \ref{sec:tools}.
+At the end, some special issues during system development are reported in the last section.

### 2013-12-29 docs/reports/finalreport/problem.tex
revising finalreport - writing apply methods of aggregation functions

@@
-\section{Problem Statement}
-The client uploads documents to the website and asks for translators in different languages.
-Based on four criteria, the system starts searching for the best three translators.
+\section{Requirements and Scenario}
+In the first step, Translators define their profiles.
+Each translator is setting a price and duration per word for each language pair.
+Then, they upload the documents which has been translated before.
+These documents are used for calculating the similarity.
+
+In order to search for a translator, the client uploads documents to the website.
+Based on four criteria, the system starts searching the best three translators.
 These criteria are cost, delivery time, frequent cooperation and text matching.
-Every criterion has also its weight which defines the importance from client’s point of view.
+Every criterion has also its weight which defines its importance from client's point of view.
 
-Each translator is proposing a price for each language pair which is used for calculating final cost.
-Delivery time is calculated based on the schedule of translator.
+Final cost is calculated based on price per word.
+Delivery time is estimated using the schedule of translator as well as duration per word.
 Finally, in order to find text matching value, the similarity between query document and previous translated documents is aggregated.
-In primitive steps of registration, every translator uploads the documents has been translated before.
-These documents are also considered for calculating the similarity.
 
 After merging the results of different criteria, the system represents the most appropriate translators to the client.
-By choosing the translator and following payment process, the translation starts.
+By choosing the translator and following payment process, the translator is informed for starting translation.
 After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator.
-At the end the proof-reader rates the translation from different aspects.
+At the end the proof-reader rates the translation.
 
-The problems and requirements addressed in the project are as follows:
+The requirements considered in the project are as follows:
 \begin{itemize}
 	\item wizard-like page for ordering process in a SPA (Single Page Application) structure.
-	\item Indexing previous-translated texts and finding an aggregation function for their similarity values with query document.
-	\item Finding and tuning a ranking function for finding the best three translators among all.
+	\item Indexing previous-translated texts and finding an aggregation function for their similarity values regarding to query document.
+	\item Developing a ranking function in order to find the best three translators among all.
 	\item Calculating delivery time based on translator's schedule.
-	\item Web API interface as well as web interface
+	\item Web as well as Web API interface.
 	\item Payment process.

### 2013-12-29 docs/reports/finalreport/report.tex
revising finalreport - writing apply methods of aggregation functions

@@
 \begin{abstract}
-The reports explains the efforts done by design and develop a translator
-retrieval system.
-The system can be defined in domain of on-line translation.
-It aims to find an appropriate translator for a client and manages the process till the last step.
-Besides, by providing a translation memory system translators can apply their previous translated texts in their new ones.
-In the project, C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used.
-It is designed based on DDD (Data Driven Design) model.
+The report explains the details of design and developing process of a translator retrieval platform.
+The platform can be defined in domain of on-line translation.
+It aims to suggest an appropriate translator to a client and manages the process of translation till the last step.
+Besides, by providing a translation memory system translators can exploit their previous translated texts in their new ones.
+C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used.
+The system is designed based on DDD (Data Driven Design) model.
 Windows Azure is also selected as deployment environment.

### 2013-12-29 docs/seminar/evaluation.tex
revising finalreport - writing apply methods of aggregation functions

@@
 \subsection{Aggregation Functions}
-TODO
+Similar to \cite{agg-gp2}, outcome of three algorithms are compared.
+Top1 and Top5 are selected as two common forms TopN aggregation algorithm.
+TopN refers to algorithm that summarizes the N top documents (i.e.
+Top1 only using the top associated document to rank the candidates).
+
+Feedbacks of Proof-readers after every translation are used as a basis for evaluating the algorithms.
+Since feedbacks are a measure for quality of translation, the more similar the ranking of algorithms to feedbacks are the better it is.
+
+The results of applying Spearman correlation is shown in Table\ref{table:Spearman}.
+As the outcome shows, GP2 outperforms the other algorithms.
+In comparison to Top1, Top5 has slightly better performance.
+The results is also partly the same based on each language-pair.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline Algorithm & Top1 & Top5 & GP2  \\
+\hline Spearman correlation & 0.049 & 0.076 & 0.14\\
+\hline
+\end{tabular}
+\caption{Comparison between algorithms and feedbacks}
+\label{table:Spearman}
+\end{center}
+\end{table}
 

### 2013-12-30 docs/seminar/casestudy.tex
revising seminar

@@
 The data flow of expert searching is depicted in Figure\ref{fig:architecture}.
-The client submits a document and searches translators of a specific target language.
-Based on query document, the framework figures out offered price, delivery time, proficiency and number of cooperation times related to each translator.
+The client submits a document and searches for translators with a specific target language.
+Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator.
 The result is processing by a ranking system and the most related translators are offered to the client.
@@
 
-\textit{Ranking} system uses L2R to return the most related translators to the query.
-The training data is provided by a group of evaluators who are familiar with business of company.
-In an evaluation system, they choose a translator between three offered ones.
-In order to prevent bias in evaluation, the translators are offered randomly and without name and picture.
-Applied method and results are described in Section \ref{sec:apply}.
+\textit{Ranking} system uses L2R to return the most related translators to the client.
+The training data is provided by a group of evaluators who are familiar with business of company using an evaluation system.
+The evaluation suggests three translators and by comparing between their factors, the evaluators choose one.
+In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture.
+Applied learning to rank methods and results are described in Section \ref{sec:apply}.
 \textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library.
 The similarity between query and indexed documents is used as a base for estimation of translator's proficiency.
-In the next step, calculated similarities are aggregated.
+In order to find a value proficiency, the similarity scores are aggregated.
 The applied aggregation function is described in Section \ref{sec:apply}.
@@
 The scheduler builds a special data structure to outperform the response time.
-The detail of the process is out of scope of the paper .At last, \textit{Profiler} accumulates personal information of translators, their preferences as well as offered price and translation duration per word.
+The detail of the process is out of scope of the paper.
+At last, \textit{Profiler} accumulates personal information, translators' preferences as well as offered price and translation duration per word.
 
-Beside translator, a proofreader selected by the client is revising the final translation.
-The proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language) as well.
+Beside translator, a proofreader selected by the client revises the final translation.
+As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).
 The assessment is defined as a value between one (very bad) to five (perfect).
-As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translation proficiency.
+As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translator's proficiency.

### 2013-12-30 docs/seminar/evaluation.tex
revising seminar

@@
 \label{sec:apply}
-In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characters and data.
+In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characteristics and data.
 
@@
 
-The results of applying Spearman correlation is shown in Table\ref{table:Spearman}.
+The result of applying Spearman correlation is shown in Table\ref{table:Spearman}.
 As the outcome shows, GP2 outperforms the other algorithms.
 In comparison to Top1, Top5 has slightly better performance.
-The results is also partly the same based on each language-pair.
+The results is also partly the same when comparing based on language-pairs.
 

### 2013-12-30 docs/seminar/introduction.tex
writing case study
revising seminar

@@
+\section{Introduction}
+\label{sec:introduction}
 The goal of expertise retrieval is to link humans to expertise areas, and vice versa.
@@
 
-The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects.
-
 With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}.
-Expertise retrieval has received increasing interest since the introduction of an expert finding task in the Text Retrieval Conference (TREC) 2005 \cite{trec2005} \cite{er-community-aware}.
+The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005} \cite{er-community-aware}.
 
@@
 They were formalized as so-called candidate models and document models.
-the candidate-based approach is also referred to as
-profile-based method in builds a textual representation of candidate experts and then rank them based on the query.
-The document models' idea is to first find documents that are relevant to the topic and then locate the experts associated with these documents \cite{er}.
+The candidate-based approach which is also referred to as profile-based method, builds a textual representation of candidate experts and then rank them based on the query.
+The document models is to first find documents that are relevant to the topic and then locate the experts associated with these documents \cite{er}.
 
@@
 
-This paper addresses the problem of searching translators as expertises.
+This paper addresses the problem of searching translators as experts.
 We have applied Learning to Rank in a candidate-based approach.

### 2013-12-30 docs/seminar/methods.tex
revising seminar

@@
 \label{sec:methods}
-In this section, we study thoroughly different methods and algorithms regarding to Aggregation Functions and Learning to Rank.
-The study will shed light on the problem of picking the most appropriate algorithm regarding to the project.
+In this section, we study different methods and algorithms regarding to Aggregation Functions and Learning to Rank.
 
 \subsection{Aggregation Functions}
+The aggregation function has a significant impact on the performance of Expert Retrieval system.
 As a usual scenario in expert retrieval systems, first each document related to an expert is scored and ranked regarding to query.
 Then, the top $N$ document scores associated with a candidate expert are aggregated in order to rank the experts.
-The aggregation function has a big impact on the performance of Expert Retrieval system.
 
-The effect of different features on aggregation function is is studied in \cite{agg-gp2}.
+The effect of different features on aggregation function is studied in \cite{agg-gp2}.
 As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$.
@@
 \subsection{Learning To Rank}
+Learning to rank refers to machine learning techniques for training the model in a ranking task.
+Due to its importance, learning to rank has been drawing broad attention in the machine learning community recently.
 TODO

### 2014-01-11 docs/reports/finalreport/architecture.tex
rivising report based on Mihai's feedback

@@
 \section{Architecture and Design}
+\label{sec:architecture}
 The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture.
-As it is depicted in Figure \ref{fig:architecture}, the system is consisted of three main layers : Interface, Business and Data Access Layer.
+As it is depicted in Figure \ref{fig:architecture}, the system consists of three main layers : Interface, Business and Data Access Layer.
 Data is passed between the layers using Model objects.
 
-Interface layer can be divided into two main parts.
-Server side and client side.
+Interface layer is divided into two main parts.
+Server and client side.
 Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model.
-It's main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice verse.
-Client side web pages are designed based on MVVM (Model-View, View, Model) model.
-Tools used for applying the model are explained in Section\ref{sec:tools}.
+Its main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice versa.
+Client-side web pages are designed based on MVVM (Model-View, View, Model) model.
+Tools used for developing the model are explained in Section \ref{sec:tools}.
 
-Using AOP (Aspect-Oriented Programming), logging, error handling and security are designed on top of other layers.
+Using AOP (Aspect-Oriented Programming), logging, error handling and security systems are designed on top of other layers.
 

### 2014-01-11 docs/reports/finalreport/development.tex
rivising report based on Mihai's feedback

@@
 \section{Development}
+\label{sec:development}
 In this section, some special issues related to development of different components are described.
@@
 Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS.
-Complex business of the company in applying query, offering translators and purchasing order urges using design models and standards.
+By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps.
+The system screen-shots of ordering process are shown in Figure\ref{fig:order-1}, Figure\ref{fig:order-2} and Figure\ref{fig:order-3}.
+The payment process shown in Figure\ref{fig:order-3} is verified by a third-party service which supports different payment cards.
+
 \subsection{Machine Learning's Data Accumulating}
-In order to tackle the problem of translator's ranking, a data accumulating system is designed.
-Similar to Order, based on query document it offers three translators and stores client's choice.
-The data gathered by the system is used in a Machine Learning program using Learning to Rank algorithms.
-It aims to discover the underlying pattern for proposing the translators.
+In order to tackle the problem of translators ranking, a system similar to Order is designed.
+The system aims to accumulate data for Learning To Rank process.
+Based on query document, it offers three translators and stores client's (evaluator's) choice.
+In contrast to Order system, it eliminates the pictures and names of translators which prevents bias in final answers by estimators and puts emphasis on the presented criteria.
+A screen-shot of the system related to selecting the translators is shown in Figure\ref{fig:dataaccumulating}.
+In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators.
 The details of the project is described in seminar lecture related to the project.
-In contrast to Order system, the system eliminates translator's picture and name which prevents bias in final answer by estimator and puts emphasis on the presented criteria.
+
 \subsection{Text Matching}
-Using Lucene, translator's documents are stored regarding to their languages.
+Using Lucene, the documents of translators are categorized, indexed and stored based on their languages.
 In order to achieve the final text matching value, the similarity between each document and query document is calculated.
@@
 As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
+
 \subsection{Translation Memory}
-As it's mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations.
-In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in another language.
-Although the algorithm is very error-prone specially for complex texts, adding dictionary and using rather simple and straightforward texts lead to more reasonable results.
+As it is mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations.
+In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language.
+While the algorithm tends to be error-prone in its basic version for complex texts, by extending dictionary and using rather simple and straightforward texts, reasonable aligned sentences were achieved.
 At the end, Lucene indexes the text and provides searching abilities.
+
+\subsection{Scheduling}
+The system is also designed following the SPA idea and using Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule of an arbitrary translator.
+
+\subsection{Chat}
+Using Signal-R capabilities, the Chat system is designed and developed. Related interfaces for meeting room as well as chatting with help-desk user are shown in Figure\ref{fig:chat}.
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
+\caption{Order - entering primitive data
+\label{fig:order-1}}
+\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
+\caption{Order - selecting translator
+\label{fig:order-2}}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
+\caption{Order - payment process
+\label{fig:order-3}}
+\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
+\caption{Data Accumulating - selecting translator
+\label{fig:dataaccumulating}}
+\end{center}
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=\figurescaling]{figures/chat.jpg}
+\caption{Scheduling
+\label{fig:scheduling}}
+\includegraphics[scale=\figurescaling]{figures/chat.jpg}
+\caption{Chat system
+\label{fig:chat}}
+\end{center}
+\end{figure}

### 2014-01-11 docs/reports/finalreport/introduction.tex
rivising report based on Mihai's feedback

@@
 
-Using the platform, regardless to geographical location of translators and clients, they can communicate and proceed a translation process.
+Using the platform, regardless of geographical location of translators and clients, they can communicate and proceed with translation.
 It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.
 
-In the following, first I describe system requirements.
-Then system architecture and design are explained.
-Tools and Technologies applied in the platform are Section \ref{sec:tools}.
-At the end, some special issues during system development are reported in the last section.
+The developed platform mainly consists of two parts.
+First, storing profiles of translators by providing registration as well as scheduling possibilities.
+Additionally, assisting them during translation process by offering a simple translation memory system.
+Second, providing a platform for clients to search and hire the translators and purchase the orders.
+Some complexities like text processing and expert ranking are tackled in the second part.
+
+The remain of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail.
+Then in Section \ref{sec:architecture}, system architecture as well as design methods are explained.
+Applied tools and technologies following with a short description are introduced in Section \ref{sec:tools}.
+At the end in Section \ref{sec:development}, by demonstrating the final product in some screen-shots, specific issues in system development are reported.

### 2014-01-11 docs/reports/finalreport/problem.tex
rivising report based on Mihai's feedback

@@
-\section{Requirements and Scenario}
-In the first step, Translators define their profiles.
-Each translator is setting a price and duration per word for each language pair.
-Then, they upload the documents which has been translated before.
-These documents are used for calculating the similarity.
+\section{Scenario and Requirements}
+\label{sec:scenario}
+In this section, first the usual system scenario is described in detail. Then, some specific requirements related to system development are specified.
 
-In order to search for a translator, the client uploads documents to the website.
-Based on four criteria, the system starts searching the best three translators.
+By registering in the platform, the translators start to declare their profiles.
+Regarding to each language pair, the price and duration per word is set.
+In the next step, the translators upload their previous-translated documents.
+The documents are processed and used in text matching as well as  translation memory systems.
+As the last step, the translators fill the time table using schedule system.
+They specify the time slots in which they are ready to work and potentially can be hired by clients.
+
+The client starts searching for translators by uploading a document.
+Based on four criteria, the system searches and retrieves the three most-related translators.
 These criteria are cost, delivery time, frequent cooperation and text matching.
-Every criterion has also its weight which defines its importance from client's point of view.
+Related to each criterion, a weight is defined which specifies importance of the criterion from client's point of view.
 
-Final cost is calculated based on price per word.
-Delivery time is estimated using the schedule of translator as well as duration per word.
-Finally, in order to find text matching value, the similarity between query document and previous translated documents is aggregated.
+Using the profiles of the translators as well client's document, the value for each criteria is estimated.
+Cost is calculated based on price per word and the number of words in the document.
+Delivery time is estimated using the schedule of translator, duration per word as well as the number of words.
+Finally, text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous-translated documents.
 
-After merging the results of different criteria, the system represents the most appropriate translators to the client.
-By choosing the translator and following payment process, the translator is informed for starting translation.
+After achieving the values of different criteria, the system ranks the translators and represents the three most-related ones to the client.
+The client chooses one and follows payment process.
+By purchasing the order, the platform informs the translator and asks for confirmation.
+During translation, the client and translator are in contact using a chat system.
 After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator.
-At the end the proof-reader rates the translation.
+At the end, the proof-reader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).
 
@@
 \begin{itemize}
-	\item wizard-like page for ordering process in a SPA (Single Page Application) structure.
-	\item Indexing previous-translated texts and finding an aggregation function for their similarity values regarding to query document.
+	\item Wizard-like page for purchasing the order in a SPA (Single Page Application) structure.
+	\item Indexing previous-translated texts and finding a function for aggregating their similarity values regarding to query document.
 	\item Developing a ranking function in order to find the best three translators among all.
 	\item Calculating delivery time based on translator's schedule.
-	\item Web as well as Web API interface.
-	\item Payment process.
+	\item Web-Page as well as Web-API interface.
+	\item Supporting payment process for different payment cards and methods.
 	\item Short response time.

### 2014-01-11 docs/reports/finalreport/architecture.tex
proof reading

@@
 Interface layer is divided into two main parts.
-Server and client side.
-Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model.
+Server- and client-side.
+Server-side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model.
 Its main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice versa.
@@
 
-Using AOP (Aspect-Oriented Programming), logging, error handling and security systems are designed on top of other layers.
+Using AOP (Aspect-Oriented Programming), logging, error handling and security systems are developed on top of other layers.
 
-As well as mentioned architectural patterns, following design patterns are used:
+As well as mentioned architectural design patterns, following implementation design patterns are used:
 \begin{itemize}
@@
 \begin{center}
-\includegraphics[scale=0.9]{figures/architecture.jpg}
+\includegraphics[scale=0.8]{figures/architecture.jpg}
 \caption{System Architecture

### 2014-01-11 docs/reports/finalreport/development.tex
proof reading

@@
 \label{sec:development}
-In this section, some special issues related to development of different components are described.
+In this section, some special issues during the development of the platform are described.
 
 \subsection{Order}
-Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS.
+Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS.
 By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps.
@@
 In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators.
-The details of the project is described in seminar lecture related to the project.
+The details are described in seminar lecture related to the project.
 
@@
 Using Lucene, the documents of translators are categorized, indexed and stored based on their languages.
-In order to achieve the final text matching value, the similarity between each document and query document is calculated.
-The main problem here is the way to  aggregate result scores.
-As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
+In the next step, the similarity between each document and query document is calculated.
+In order to achieve the final text matching value, the calculated similarities should be aggregated.
+As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented and used.
 
@@
 In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language.
-While the algorithm tends to be error-prone in its basic version for complex texts, by extending dictionary and using rather simple and straightforward texts, reasonable aligned sentences were achieved.
+While the algorithm tends to be error-prone in its basic version specially for complex texts, by adding dictionaries and using just rather simple and straightforward texts, reasonable aligned sentences were achieved.
 At the end, Lucene indexes the text and provides searching abilities.
@@
 \subsection{Scheduling}
-The system is also designed following the SPA idea and using Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule of an arbitrary translator.
+The system is also designed by following the SPA idea and using pure Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule web-page interface for an arbitrary translator.
 

### 2014-01-11 docs/reports/finalreport/introduction.tex
proof reading

@@
 
-Using the platform, regardless of geographical location of translators and clients, they can communicate and proceed with translation.
+Using the platform, regardless of geographical location, translators and clients can communicate and proceed the translation.
 It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.
@@
 The developed platform mainly consists of two parts.
-First, storing profiles of translators by providing registration as well as scheduling possibilities.
+First, storing profiles of translators developed in registration and  scheduling systems.
 Additionally, assisting them during translation process by offering a simple translation memory system.
 Second, providing a platform for clients to search and hire the translators and purchase the orders.
-Some complexities like text processing and expert ranking are tackled in the second part.
 
@@
 Applied tools and technologies following with a short description are introduced in Section \ref{sec:tools}.
-At the end in Section \ref{sec:development}, by demonstrating the final product in some screen-shots, specific issues in system development are reported.
+At the end in Section \ref{sec:development}, by demonstrating the final product in some system screen-shots, specific issues in system development are reported.

### 2014-01-11 docs/reports/finalreport/problem.tex
proof reading

@@
 \label{sec:scenario}
-In this section, first the usual system scenario is described in detail. Then, some specific requirements related to system development are specified.
+In this section, first the usual scenario of the system is described in detail. Then, some specific requirements related to system development are specified.
 
@@
 Cost is calculated based on price per word and the number of words in the document.
-Delivery time is estimated using the schedule of translator, duration per word as well as the number of words.
+Delivery time is estimated using the schedule of translator, duration per word and the number of words in the document.
 Finally, text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous-translated documents.

### 2014-01-11 docs/reports/finalreport/development.tex
adding new screen-shot

@@
 By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps.
-The system screen-shots of ordering process are shown in Figure\ref{fig:order-1}, Figure\ref{fig:order-2} and Figure\ref{fig:order-3}.
-The payment process shown in Figure\ref{fig:order-3} is verified by a third-party service which supports different payment cards.
+The system screen-shots of ordering process are shown in Figure\ref{fig:order-1} and Figure\ref{fig:order-2}.
+The payment process is verified by a third-party service which supports different payment cards.
 
@@
 \label{fig:order-1}}
-\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
+\includegraphics[scale=\figurescaling]{figures/order-2.jpg}
 \caption{Order - selecting translator
@@
 \begin{center}
-\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
-\caption{Order - payment process
-\label{fig:order-3}}
-\includegraphics[scale=\figurescaling]{figures/order-1.jpg}
+\includegraphics[scale=\figurescaling]{figures/dataaccumulation.jpg}
 \caption{Data Accumulating - selecting translator
 \label{fig:dataaccumulating}}
+\includegraphics[scale=\figurescaling]{figures/chat.jpg}
+\caption{Chat system
+\label{fig:chat}}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=\figurescaling]{figures/chat.jpg}
+\includegraphics[scale=\figurescaling]{figures/scheduling.jpg}
 \caption{Scheduling
 \label{fig:scheduling}}
-\includegraphics[scale=\figurescaling]{figures/chat.jpg}
-\caption{Chat system
-\label{fig:chat}}
 \end{center}

### 2014-01-11 docs/reports/finalreport/introduction.tex
adding new screen-shot

@@
 \section{Introduction}
-As a hub for professional translation services, nativy \cite{nativy}(founded 2011 in Vienna) offers its customers top-quality translations at reasonable terms.
-
-The company works exclusively with qualified translators into their native language.
-All nativy translations are reviewed in accordance with EN $15038$, the European Quality Standard for Translation Services, and translators have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.
+As a hub for professional translation services, the platform offers its customers top-quality translations at reasonable terms.
+All translations are reviewed and have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.
 

### 2014-02-06 docs/reports/finalreport/architecture.tex
revising finalreport and paper

@@
 The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture.
-As it is depicted in Figure \ref{fig:architecture}, the system consists of three main layers : Interface, Business and Data Access Layer.
+As depicted in Figure \ref{fig:architecture}, the system consists of three main layers : Interface, Business and Data Access Layer.
 Data is passed between the layers using Model objects.
 
-Interface layer is divided into two main parts.
+The interface layer is divided into two main parts.
 Server- and client-side.
-Server-side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model.
-Its main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice versa.
-Client-side web pages are designed based on MVVM (Model-View, View, Model) model.
+The server-side which is denoted as Application Layer is following the MVVC (Model-View, View, Controller) design model.
+Its main purpose is mapping Model-View objects of the Interface Layer to Model objects and passing them to the Business Layer and vice versa.
+Client-side web pages are designed based on the MVVM (Model-View, View, Model) model.
 Tools used for developing the model are explained in Section \ref{sec:tools}.
@@
 
-As well as mentioned architectural design patterns, following implementation design patterns are used:
+As well as the mentioned architectural design patterns, the following implementation design patterns are used:
 \begin{itemize}

### 2014-02-06 docs/reports/finalreport/design.tex
revising finalreport and paper

@@
 \label{sec:tools}
-In this section, the main applied tools, technologies and libraries are briefly described following by their usage in the system.
+In this section, the main applied tools, technologies and libraries are briefly described followed by their usage in the system.
 
 \begin{itemize}
-	\item \textbf{C\texttt{\#}.NET 4.5:} As the main programming language, the project is being developed on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
+	\item \textbf{C\texttt{\#}.NET 4.5:} The main programming language, project is being developed on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
 	\item \textbf{ASP.NET 4.5:} It provides the required framework for web programming. MVC.NET is used as the main server side platform.
-	\item \textbf{MS SQL Azure:} As the system is deployed on Windows Azure platform, SQL Azure is selected as relational database.
+	\item \textbf{MS SQL Azure:} As the system is deployed on the Windows Azure platform, SQL Azure is selected as relational database.
 	\item \textbf{Windows Azure:} Some special services like Cache, Storage and Service Bus are widely used in the project.
@@
 While Lucene in Java provides more options, the .NET version is used to keep the integrity of project.
-	\item \textbf{LINQToSQL:} Regarding to high integrity of the tool with MS SQL Server, LINQToSQL is used as ORM (Object-Relational Mapping) tool.
+	\item \textbf{LINQToSQL:} Regarding to high level of integrity of the tool with MS SQL Server, LINQToSQL is used as ORM (Object-Relational Mapping) tool.
 	\item \textbf{HunAlign\cite{hunalign}:} A light library which aligns bilingual text on the sentence level.

### 2014-02-06 docs/reports/finalreport/development.tex
revising finalreport and paper

@@
 \label{sec:development}
-In this section, some special issues during the development of the platform are described.
+In this section, we describe some special issues during the development of the platform.
 
 \subsection{Order}
-Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS.
+The Order system is a full client-side web-page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS.
 By applying MVVM model, the data submitted in each step is stored in View-Model and used in the next steps.
-The system screen-shots of ordering process are shown in Figure\ref{fig:order-1} and Figure\ref{fig:order-2}.
+The system screen-shots from the ordering process are shown in Figure \ref{fig:order-1} and Figure \ref{fig:order-2}.
 The payment process is verified by a third-party service which supports different payment cards.
@@
 \subsection{Machine Learning's Data Accumulating}
-In order to tackle the problem of translators ranking, a system similar to Order is designed.
-The system aims to accumulate data for Learning To Rank process.
-Based on query document, it offers three translators and stores client's (evaluator's) choice.
-In contrast to Order system, it eliminates the pictures and names of translators which prevents bias in final answers by estimators and puts emphasis on the presented criteria.
-A screen-shot of the system related to selecting the translators is shown in Figure\ref{fig:dataaccumulating}.
+In order to tackle the problem of ranking translators, a system similar to Order is designed.
+The system aims to accumulate data for a Learning To Rank process.
+Based on the query document, it offers three translators and stores the client's (evaluator's) choice.
+In contrast to the Order system, it eliminates the pictures and names of translators in order to reduce clients' bias in the final answer and puts emphasis on the presented criteria.
+A screen-shot of the system related to selecting the translators is shown in Figure \ref{fig:dataaccumulating}.
 In the next step, the data gathered by the system is applied on Learning to Rank algorithms which aim to discover the underlying pattern for proposing the best translators.
@@
 In order to achieve the final text matching value, the calculated similarities should be aggregated.
-As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented and used.
+We use GP2\cite{gp2} algorithm to aggregate similarity values.
 
 \subsection{Translation Memory}
-As it is mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations.
-In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language.
+As mentioned before, the aim of a Translation Memory system is helping the translators to exploit their previous translated texts in their new translations.
+In order to develop the system, first the HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in the other language.
 While the algorithm tends to be error-prone in its basic version specially for complex texts, by adding dictionaries and using just rather simple and straightforward texts, reasonable aligned sentences were achieved.
@@
 \subsection{Scheduling}
-The system is also designed by following the SPA idea and using pure Java-Script libraries and Web-API. Figure\ref{fig:scheduling} depicts the schedule web-page interface for an arbitrary translator.
+The scheduling system is also designed by following the SPA idea and using pure Java-Script libraries and Web-API.
+Figure \ref{fig:scheduling} depicts the schedule web-page interface for an arbitrary translator.
 
 \subsection{Chat}
-Using Signal-R capabilities, the Chat system is designed and developed. Related interfaces for meeting room as well as chatting with help-desk user are shown in Figure\ref{fig:chat}.
+Using Signal-R capabilities, we develop the Chat system. Related interfaces for meeting room as well as chatting with help-desk user are shown in Figure \ref{fig:chat}.
 

### 2014-02-06 docs/reports/finalreport/introduction.tex
revising finalreport and paper

@@
 As a hub for professional translation services, the platform offers its customers top-quality translations at reasonable terms.
-All translations are reviewed and have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.
+All translators have to provide evidence of the required qualifications by means of their résumé.
 
-Using the platform, regardless of geographical location, translators and clients can communicate and proceed the translation.
-It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.
+Using the platform, regardless of geographical location, translators and clients can communicate and produce the translation.
+The platform facilitates translating text to even not-so-popular languages.
 
-The developed platform mainly consists of two parts.
-First, storing profiles of translators developed in registration and  scheduling systems.
-Additionally, assisting them during translation process by offering a simple translation memory system.
-Second, providing a platform for clients to search and hire the translators and purchase the orders.
+The developed platform can mainly be divided into two parts.
+First, translator platform which consists of registration,  scheduling and translation memory system.
+Second, client platform which facilitates searching and hiring the translators as well as purchasing the orders.
 
-The remain of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail.
-Then in Section \ref{sec:architecture}, system architecture as well as design methods are explained.
-Applied tools and technologies following with a short description are introduced in Section \ref{sec:tools}.
-At the end in Section \ref{sec:development}, by demonstrating the final product in some system screen-shots, specific issues in system development are reported.
+The remainder of the report is organized as follows: In Section \ref{sec:scenario}, system requirements and usual scenarios are described in detail.
+Then in Section \ref{sec:architecture}, the system architecture as well as design methods are explained.
+Section \ref{sec:tools} introduces the tools and technologies we applied.
+Section \ref{sec:development} reports specific issues in the development of the system by demonstrating the final product in a series of system screen-shots.

### 2014-02-06 docs/reports/finalreport/problem.tex
revising finalreport and paper

@@
 \label{sec:scenario}
-In this section, first the usual scenario of the system is described in detail. Then, some specific requirements related to system development are specified.
+In this section, first the usual scenario of the system is described in detail. Then, the specific requirements related to system development are specified.
 
@@
 Regarding to each language pair, the price and duration per word is set.
-In the next step, the translators upload their previous-translated documents.
+In the next step, the translators upload their previous translated documents.
 The documents are processed and used in text matching as well as  translation memory systems.
@@
 The client starts searching for translators by uploading a document.
-Based on four criteria, the system searches and retrieves the three most-related translators.
+Based on four criteria, the system searches and retrieves the three most relevant translators.
 These criteria are cost, delivery time, frequent cooperation and text matching.
-Related to each criterion, a weight is defined which specifies importance of the criterion from client's point of view.
+Related to each criterion, a weight is defined which specifies the importance of the criterion from the client's point of view.
 
@@
 Cost is calculated based on price per word and the number of words in the document.
-Delivery time is estimated using the schedule of translator, duration per word and the number of words in the document.
-Finally, text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous-translated documents.
+Delivery time is estimated using the schedule of the translator, duration per word and the number of words in the document.
+Finally, a text matching value is computed by processing the text and aggregating the similarity values between the query document and the previous translated documents of all the translators for the desired language pair.
 
-After achieving the values of different criteria, the system ranks the translators and represents the three most-related ones to the client.
-The client chooses one and follows payment process.
+After having calculated the values of different criteria, the system ranks the translators and represents the three most relevant ones to the client.
+The client chooses one and follows the payment process.
 By purchasing the order, the platform informs the translator and asks for confirmation.
 During translation, the client and translator are in contact using a chat system.
-After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator.
-At the end, the proof-reader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).
+After finishing the translation, a qualified proof-reader chosen by the client revises the text and may send some corrections to the translator.
+At the end, the proof-reader assesses the quality of the translation from different points of view (grammar, style, accuracy, content and language) by giving a score (1-5) of each of them.
 

### 2014-02-06 docs/reports/finalreport/report.tex
rivising report based on Mihai's feedback
revising finalreport and paper

@@
+\newcommand{\figurescaling}{0.7}
 \input{config}
@@
 The report explains the details of design and developing process of a translator retrieval platform.
-The platform can be defined in domain of on-line translation.
-It aims to suggest an appropriate translator to a client and manages the process of translation till the last step.
-Besides, by providing a translation memory system translators can exploit their previous translated texts in their new ones.
-C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used.
-The system is designed based on DDD (Data Driven Design) model.
-Windows Azure is also selected as deployment environment.
+The platform's objective is to suggest an appropriate translator to a client.
+It manages the process of translation until the last step.
+Additionally, by providing a translation memory system translators can exploit their previous translated texts in their new ones.
+C\texttt{\#}.NET and MS SQL SERVER are used as main platform and Lucene.NET is the text processor.
+The system is designed based on Data Driven Design (DDD) model.
+Windows Azure is the deployment environment.
 \end{abstract}
@@
 
+\section{Conclusion}
+\label{sec:conclusion}
+In this report, we explain different aspects of implementing a translator retrieval system. We report designed architecture, applied tool as well as problems and pitfalls during development.
+
+The project bring us deep understanding on development of an expert retrieval system in a web-based platform.
+During the system implementation, we confront many problems in the area of text processing, searching and information retrieval.
+Additionally, we try to apply the best practice on system design and develop regarding to software engineering point of view.
+\newpage
+
+\listoffigures
 \bibliographystyle{plain}

### 2014-02-06 docs/seminar/casestudy.tex
revising finalreport and paper

@@
 Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator.
-The result is processing by a ranking system and the most related translators are offered to the client.
+The result is processed by a ranking system and the most related translators are offered to the client.
 
-As it is shown in Figure\ref{fig:architecture}, the essential components of the framework are \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiler}.
+As it is shown in Figure \ref{fig:architecture}, the essential components of the framework are \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiler}.
 
@@
 In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture.
-Applied learning to rank methods and results are described in Section \ref{sec:apply}.
+Applied learning to rank methods and results are described in Section \ref{sec:methods}.
 \textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library.
 The similarity between query and indexed documents is used as a base for estimation of translator's proficiency.
-In order to find a value proficiency, the similarity scores are aggregated.
+In order to find proficiency value, the similarity scores are aggregated.
 The applied aggregation function is described in Section \ref{sec:apply}.
 \textit{Scheduler} system figures out the delivery time based on timetable of translators.
-The scheduler builds a special data structure to outperform the response time.
+The scheduler builds a special data structure to calculate the response time.
 The detail of the process is out of scope of the paper.
@@
 As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).
-The assessment is defined as a value between one (very bad) to five (perfect).
+The assessment is defined as a value between $1$ (very bad) and $5$ (perfect).
 As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translator's proficiency.

### 2014-02-06 docs/seminar/evaluation.tex
revising finalreport and paper

--- 2013-12-28 docs/seminar/evaluation.tex
@@
 \label{sec:apply}
-In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characters and data.
+In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characteristics and data.
 
 \subsection{Aggregation Functions}
-TODO
+In order to compare different aggregation functions, similar to \citet{agg-gp2} three algorithms are selected.
+$GP2$ as well as $Top1$ and $Top5$ which are two common forms of $TopN$ aggregation algorithm.
+$TopN$ refers to algorithm that summarizes the $N$ top documents (i.e.
+$Top1$ only using the top associated document to rank the candidates).
+
+Feedbacks of proof-readers after every translation are used as a basis for evaluating the algorithms.
+Since feedbacks are a measure for quality of translation, the more similar the ranking of algorithms to feedbacks are the better it is.
+
+The calculation is done based on $181$ records of purchased orders.
+The coefficient values of applying Pearson Correlation ($r$) and Spearman's Rank Order Correlation ($r_s$) are shown in Table \ref{table:Spearman}.
+TODO: Significance Test .
+
+The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
+Nevertheless among the introduced algorithms, $GP2$ outperforms the others.
+In comparison to $Top1$, $Top5$ has slightly better performance.
+The results are also nearly the same when comparing based on language-pairs.
+
+\begin{table}
+\begin{center}
+\scalebox{1.2}{
+\begin{tabular}{p{1cm}|c|c|c|}
+\cline{2-4} & Top1 & Top5 & GP2  \\
+\hline \multicolumn{1}{ |c| }{$r$} & 0.018 & 0.063 & 0.117\\
+\hline \multicolumn{1}{ |c| }{$r_s$} & 0.052 & 0.087 & 0.145\\
+\hline
+\end{tabular}
+}
+\caption{Comparison between algorithms and feedbacks}
+\label{table:Spearman}
+\end{center}
+\end{table}
 

### 2014-02-06 docs/seminar/introduction.tex
revising finalreport and paper

@@
 The goal of expertise retrieval is to link humans to expertise areas, and vice versa.
-In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er} \cite{er-community-aware}.
+In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \citep{er, er-community-aware}.
 
 With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}.
-The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005} \cite{er-community-aware}.
+The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.
 
-Two principal approaches are proposed in \cite{trec2005} based on probabilistic language modeling techniques.
+Two principal approaches are proposed by \citet{trec2005} based on probabilistic language modeling techniques.
 They were formalized as so-called candidate models and document models.
-The candidate-based approach which is also referred to as profile-based method, builds a textual representation of candidate experts and then rank them based on the query.
-The document models is to first find documents that are relevant to the topic and then locate the experts associated with these documents \cite{er}.
+The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query.
+The document models first find documents relevant to the topic and then locate the experts associated with these documents \citep{er}.
 
@@
 In recent years, Learning to Rank (L2R) has been studied extensively specially for document retrieval.
-It refers to machine learning techniques for training the model in a ranking task \cite{er}.
-In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \cite{l2r-intro}.
+It refers to machine learning techniques for training the model in a ranking task \citep{er}.
+In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \citep{l2r-intro}.
 
-As well as ranking techniques, aggregation functions have a solid effect on the performance of IR systems. Aggregate tasks are those where documents' similarities are not
+As well as ranking techniques, aggregation functions have a significant effect on the performance of IR systems. Aggregate tasks are those where documents' similarities are not
 the final outcome, but instead an intermediary component.
@@
 We have applied Learning to Rank in a candidate-based approach.
-Besides, different aggregation algorithms related to documents of translators has been studied.
+Additionally, different aggregation algorithms related to documents of translators have been studied.
 

### 2014-02-06 docs/seminar/methods.tex
revising finalreport and paper

@@
 
-The effect of different features on aggregation function is studied in \cite{agg-gp2}.
+The effect of different features on aggregation function is studied in \citet{agg-gp2}.
 As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$.
@@
 
-Macdonald et al.\cite{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise.
+\citet{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise.
 Eleven data fusion as well as three statistically different document weighting were tested.
@@
 
-Later on, focusing on related features discussed before Cummins et al.\cite{agg-gp2} comes up with a novel idea.
+Later on, focusing on related features discussed before \citet{agg-gp2} introduces a new aggregation method.
 It uses genetic programming to learn a formula for the weights of document associations within the candidate profiles.

### 2014-02-11 docs/reports/finalreport/report.tex
adding significance test results

@@
 \begin{abstract}
-The report explains the details of design and developing process of a translator retrieval platform.
+The report explains the details of design and develop of a translator retrieval platform.
 The platform's objective is to suggest an appropriate translator to a client.
@@
 Additionally, by providing a translation memory system translators can exploit their previous translated texts in their new ones.
-C\texttt{\#}.NET and MS SQL SERVER are used as main platform and Lucene.NET is the text processor.
+C\texttt{\#}.NET and MS SQL SERVER are used as main programming platforms and Lucene.NET is the text processor.
 The system is designed based on Data Driven Design (DDD) model.
@@
 \input{introduction}
-\newpage
 \input{problem}
-\newpage
 \input{architecture}
-\newpage
 \input{design}
-\newpage
 \input{development}
-\newpage
 

### 2014-02-11 docs/seminar/evaluation.tex
adding significance test results

@@
 
-The calculation is done based on $181$ records of purchased orders.
-The coefficient values of applying Pearson Correlation ($r$) and Spearman's Rank Order Correlation ($r_s$) are shown in Table \ref{table:Spearman}.
-TODO: Significance Test .
+In order to calculate the correlation value, we applied Spearman Rank Order and Kendall Rank Correlation as two common methods.
+Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using $181$ records of purchased orders.
+Table \ref{table:signtest} represents the Significance Test of both methods calculated by R.
 
+As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kandell's.
 The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
-Nevertheless among the introduced algorithms, $GP2$ outperforms the others.
+TODO about significance test??.
+
+Comparing the algorithms, $GP2$ outperforms the others in both correlation tests.
 In comparison to $Top1$, $Top5$ has slightly better performance.
@@
 \cline{2-4} & Top1 & Top5 & GP2  \\
-\hline \multicolumn{1}{ |c| }{$r$} & 0.018 & 0.063 & 0.117\\
-\hline \multicolumn{1}{ |c| }{$r_s$} & 0.052 & 0.087 & 0.145\\
+\hline \multicolumn{1}{ |c| }{$r_s$} & 0.052 & 0.089 & 0.145\\
+\hline \multicolumn{1}{ |c| }{$\tau$} & 0.034 & 0.059 & 0.102\\
 \hline
@@
 }
-\caption{Comparison between algorithms and feedbacks}
-\label{table:Spearman}
+\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks}
+\label{table:correlation}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\scalebox{1.2}{
+\begin{tabular}{p{1cm}|c|c|c|}
+\cline{2-4} & Top1 & Top5 & GP2  \\
+\hline \multicolumn{1}{ |c| }{$r_s$} & 0.4866 & 0.2295 & 0.05038\\
+\hline \multicolumn{1}{ |c| }{$\tau$} & 0.5157 & 0.2562 & 0.05263\\
+\hline
+\end{tabular}
+}
+\caption{P-Value of Significance of Correlation Test Algorithms}
+\label{table:signtest}
 \end{center}

### 2014-02-18 docs/seminar/methods.tex
l2r part

@@
 Due to its importance, learning to rank has been drawing broad attention in the machine learning community recently.
-TODO
+
+In learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied.
+As \citet{l2r-intro} points out the relation between learning to rank and ordinal classification, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
+
+One primitive step in accumulating data required for learning to rank, is relevance judgment done by human annotators. \citet{l2r-book} introduces three main strategies as follows.
+\begin{itemize}
+\item \textit{Relevance degree}: It specifies whether an object is relevant or not to the query.
+It can be either in binary judgment or by specifying the degree of relevance (e.g., Perfect, Excellent, Good, Fair, or Bad).
+\item \textit{Pairwise preference}: A pair of objects are compared in order to specify which one is more relevant with regards to a query.
+\item \textit{Total order}: The total order of all object with respect to a query is specified.
+\end{itemize}
+
+Among the three mentioned kinds of judgments, since the first is the easiest to obtain, it is the most popularly used judgment. While the third kind is more accurate but tedious for human annotators.
+
+The learning to rank techniques are categorized in three main groups: \textit{Pointwise}, \textit{Pairwise} and \textit{Listwise}.
+
+In the pointwise approach, the ranking problem is transformed to classification, regression or ordinal classification.
+Therefore, the group structure of ranking is ignored in this approach \citep{l2r-intro}.
+
+The pairwise approach transforms the ranking problem into pairwise classification or regression.
+In fact, it cares about the relative order between two documents.
+In the pairwise approach, the group structure of ranking is also ignored \citep{l2r-intro}.
+Here is a brief explanation of some of widely used pairwise algorithms:
+
+\begin{itemize}
+\item \textit{RankNet} \citep{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
+\item \textit{RankBoost} \citep{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over document pairs.
+\item \textit{LambdaRank} \citep{l2r-lambdarank}: It considers the evaluation measures to set its pair weight.
+In particular, the evaluation measures (which are position based) are directly used to define the gradient with respect to each document pair in the training process.
+\item \textit{LambdaMART} \citep{l2r-lambdamart}: It combines the strengths of boosted tree classification and \textit{LambdaRank}.
+\end{itemize}
+
+The listwise approach takes the entire set of documents associated with a query in the training data as the input and predicts their ground truth labels \citep{l2r-book}.
+The group structure of ranking is maintained and
+ranking evaluation measures can be more directly incorporated into the loss functions in learning \citep{l2r-intro}. In the following, two common listwise algorithms are briefly discussed:
+
+\begin{itemize}
+\item \textit{AdaRank} \citep{l2r-adarank}: It applies the evaluation measures on the framework of Boosting and focuses on effectively optimization.
+\item \textit{ListNet} \citep{l2r-listnet}: It uses different probability distributions in order to define the loss function.
+\end{itemize}
+
+As the different data-set are compared in \citet{l2r-book}, listwise techniques are in general the most effective among the others.
+However, the choice of the learning evaluation measure and the rank cutoff may have a noticeable impact on the effectiveness of the learned model \citep{l2r-when}.
+
+A highly important point in all kinds of information retrieval systems is evaluation of results.
+The evaluation on the performance of a ranking model is carried out by comparison between the ranking lists output by the model and the ranking lists given as the ground truth \citep{l2r-intro}.Some common IR evaluation methods like Mean average precision (MAP), [Normalized] Discounted Cumulative Gain ([N]DCG), Mean Reciprocal Rank (MRR) are also widely user in leaning to rank evaluation.
+Among the mentioned metrics, DCG/NDCG is the only one used for graded relevance.
+
+Recently, \citet{l2r-err} have proposed a new evaluation metrics called Expected Reciprocal Rank (ERR) which claims to model user's satisfaction with search results better than the DCG metric.
+\citet{l2r-err} addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it.
+It asserts that based on research on modeling user click behavior \citep{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list.
+In other words, it assumes that a user is more likely to stop browsing if they have already seen one or more highly relevant documents.
+By presenting ERR formula in \cite{l2r-err}, it claims that results reflects real user browsing behavior better and quantifies user satisfaction more accurately than DCG.

### 2014-02-18 docs/seminar/evaluation.tex
accomplishing TODOs

@@
 
-As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kandell's.
+As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kendall's.
 The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
-TODO about significance test??.
+Regarding to P-Value of significance test shown in Table \ref{table:signtest}, a meaningful relation between GP2 and feedbacks can be considered.
+Top1 which has the worst values in the table shows a meaningless and near random correlation though.
 

### 2014-02-23 docs/seminar/evaluation.tex
adding result l2r table
random ranker

@@
 \subsection{Learning To Rank}
-TODO
+In order to accumulate required data to achieve translators' ranking model, we conduct a survey using eight human annotators.
+Each question of survey represents a situation in which three translators each with four criteria are proposed.
+Based on \textit{total order} strategy, annotators should rate them from one to three.
+The accumulated data has $400$ situations consists of $1200$ annotations.
+
+In order to apply Learning to Rank algorithms on data, we use RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib}.
+Each method is calculated using 10-Fold Cross-Validation by splitting the data in train, validation and test datasets.
+We select $5$ learning to rank methods, three pairwise and two listwise.
+
+In order to evaluate the results, NDCG and ERR measures are selected.
+
+In order to evaluate the results, we need to choose an evaluation measure which applies on whole the list (with $3$ items) and not a portion of that.
+Therefore just relevance grading evaluation measures like DCG, NDCG and ERR can be used.
+In current study, we use NDGC and ERR both with rank position at $3$.
+
+TODO discussion about the results.
+
+\begin{table}
+\begin{center}
+\scalebox{1.2}{
+\begin{tabular}{|c|c|c|c|c|}
+\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
+\cline{2-5} & Result & Random & Result & Random \\
+\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
+\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
+\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
+\hline LambdaMART & \textbf{0.93} & 0.832 & \textbf{0.447} & 0.373 \\
+\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
+\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
+\hline
+\end{tabular}
+}
+\caption{Results of Applying Learning to Rank Methods based on NDCG and ERR evaluation measures}
+\label{table:l2rresult}
+\end{center}
+\end{table}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.5]{figures/l2rdiagram.png}
+\caption{Learning to Rank Results
+\label{fig:l2rdiagram}}
+\end{center}
+\end{figure}

### 2014-02-23 ciir/umass/edu/learning/RANKER_TYPE.java

@@ -1,0 +1,14 @@
+/*===============================================================================
+ * Copyright (c) 2010-2012 University of Massachusetts.  All Rights Reserved.
+ *
+ * Use of the RankLib package is subject to the terms of the software license set 
+ * forth in the LICENSE file included with this software, and also available at
+ * http://people.cs.umass.edu/~vdang/ranklib_license.html
+ *===============================================================================
+ */
+
+package ciir.umass.edu.learning;
+
+public enum RANKER_TYPE {
+	MART, RANKBOOST, RANKNET, ADARANK, COOR_ASCENT, LAMBDARANK, LAMBDAMART, LISTNET, RANDOM_FOREST, LINEAR_REGRESSION, RANDOM_RANK
+}

### 2014-02-23 ciir/umass/edu/learning/RandomRank.java

@@ -1,0 +1,67 @@
+/*===============================================================================
+ * Copyright (c) 2010-2012 University of Massachusetts.  All Rights Reserved.
+ *
+ * Use of the RankLib package is subject to the terms of the software license set 
+ * forth in the LICENSE file included with this software, and also available at
+ * http://people.cs.umass.edu/~vdang/ranklib_license.html
+ *===============================================================================
+ */
+
+package ciir.umass.edu.learning;
+
+import java.util.List;
+import java.util.Random;
+
+import ciir.umass.edu.metric.MetricScorer;
+
+public class RandomRank extends Ranker {
+
+	public RandomRank()
+	{		
+	}
+	public RandomRank(List<RankList> samples, int[] features, MetricScorer scorer)
+	{
+		super(samples, features, scorer);
+	}
+	public void init()
+	{
+		PRINTLN("Initializing... [Done]");
+	}
+	public void learn()
+	{
+		PRINTLN("--------------------------------");
+		PRINTLN("Training starts...");
+		
+		PRINTLN("---------------------------------");
+		PRINTLN("Finished sucessfully.");
+	}
+	public double eval(DataPoint p)
+	{
+		Random r = new Random();
+		return r.nextDouble();
+	}
+	public Ranker clone()
+	{
+		return new RandomRank();
+	}
+	public String toString()
+	{
+		return "";
+	}
+	public String model()
+	{
+		return "";
+	}
+	public void load(String fn)
+	{
+		
+	}
+	public void printParameters()
+	{
+		PRINTLN("NO PARAM");
+	}
+	public String name()
+	{
+		return "Random Rank";
+	}
+}

### 2014-02-23 ciir/umass/edu/learning/RankerFactory.java

@@ -1,0 +1,116 @@
+/*===============================================================================
+ * Copyright (c) 2010-2012 University of Massachusetts.  All Rights Reserved.
+ *
+ * Use of the RankLib package is subject to the terms of the software license set 
+ * forth in the LICENSE file included with this software, and also available at
+ * http://people.cs.umass.edu/~vdang/ranklib_license.html
+ *===============================================================================
+ */
+
+package ciir.umass.edu.learning;
+
+import java.io.BufferedReader;
+import java.io.FileInputStream;
+import java.io.InputStreamReader;
+import java.util.HashMap;
+import java.util.List;
+
+import ciir.umass.edu.learning.boosting.AdaRank;
+import ciir.umass.edu.learning.boosting.RankBoost;
+import ciir.umass.edu.learning.neuralnet.LambdaRank;
+import ciir.umass.edu.learning.neuralnet.ListNet;
+import ciir.umass.edu.learning.neuralnet.RankNet;
+import ciir.umass.edu.learning.tree.MART;
+import ciir.umass.edu.learning.tree.LambdaMART;
+import ciir.umass.edu.learning.tree.RFRanker;
+import ciir.umass.edu.metric.MetricScorer;
+
+/**
+ * @author vdang
+ * 
+ * This class implements the Ranker factory. All ranking algorithms implemented have to be recognized in this class. 
+ */
+public class RankerFactory {
+
+	protected Ranker[] rFactory = new Ranker[]{new MART(), new RankBoost(), new RankNet(), new AdaRank(), new CoorAscent(), new LambdaRank(), new LambdaMART(), new ListNet(), new RFRanker(), new LinearRegRank(), new RandomRank()};
+	protected static HashMap<String, RANKER_TYPE> map = new HashMap<String, RANKER_TYPE>();
+	
+	public RankerFactory()
+	{
+		map.put(createRanker(RANKER_TYPE.MART).name().toUpperCase(), RANKER_TYPE.MART);
+		map.put(createRanker(RANKER_TYPE.RANKNET).name().toUpperCase(), RANKER_TYPE.RANKNET);
+		map.put(createRanker(RANKER_TYPE.RANKBOOST).name().toUpperCase(), RANKER_TYPE.RANKBOOST);
+		map.put(createRanker(RANKER_TYPE.ADARANK).name().toUpperCase(), RANKER_TYPE.ADARANK);
[…]

### 2014-02-23 ranker/ranker.java

@@ -1,0 +1,9 @@
+
+public class ranker {
+
+	public static void main(String[] args) {
+		// TODO Auto-generated method stub
+
+	}
+
+}

### 2014-02-23 runit.java

@@ -1,0 +1,232 @@
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Random;
+
+import ciir.umass.edu.eval.Evaluator;
+import ciir.umass.edu.features.Normalizer;
+import ciir.umass.edu.features.SumNormalizor;
+import ciir.umass.edu.learning.RANKER_TYPE;
+import ciir.umass.edu.learning.RankerFactory;
+import ciir.umass.edu.metric.ERRScorer;
+import ciir.umass.edu.metric.MetricScorer;
+import ciir.umass.edu.metric.MetricScorerFactory;
+import ciir.umass.edu.utilities.MyThreadPool;
+import ciir.umass.edu.utilities.SimpleMath;
+
+
+public class runit {
+
+	public static void main(String[] args) throws IOException {
+		randomClassifier();
+			    
+	    //saveFile(loadFile(), 5);
+	}
+	
+	private static StringBuilder loadFile() throws IOException
+	{
+		BufferedReader br = new BufferedReader(new FileReader("l2r\\data\\train_standardized.letor"));
+		StringBuilder sb = new StringBuilder();
+		
+	    try {
+	    	String line1 = br.readLine();
+	        String line2 = br.readLine();
+	        String line3 = br.readLine();
+        
+	        while ((line1 != null) && (line2 != null) && (line3 != null)) {
+	        	int[] rndRank = getRandomRank();
+		        
+		        line1 = rndRank[0] + line1.substring(1);
+		        line2 = rndRank[1] + line2.substring(1);
+		        line3 = rndRank[2] + line3.substring(1);
+
+		        sb.append(line1);
+	            sb.append(System.lineSeparator());
+	            sb.append(line2);
+	            sb.append(System.lineSeparator());
+	            sb.append(line3);
+	            sb.append(System.lineSeparator());
+	            
+	            line1 = br.readLine();
+		        line2 = br.readLine();
+		        line3 = br.readLine();
+	        }
+	    } finally {
+	        br.close();
+	    }
+	    return sb;
+	}
+	
+	private static int[] getRandomRank()
+	{
+		int[] res = new int[3];
[…]

### 2014-02-25 docs/seminar/casestudy.tex
revising

@@
 Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator.
-The result is processed by a ranking system and the most related translators are offered to the client.
+The ranking system processes the calculated values and the offers the most related translators to the client.
 
@@
 
-\textit{Ranking} system uses L2R to return the most related translators to the client.
-The training data is provided by a group of evaluators who are familiar with business of company using an evaluation system.
-The evaluation suggests three translators and by comparing between their factors, the evaluators choose one.
+The \textit{Profiler} is responsible for accumulating personal information, translators' preferences, offered price and translation duration per word.
+The \textit{Ranking} system uses Learning to Rank techniques to return the most related translators to the client.
+The training data is provided by a group of annotators who are familiar with business of company using an evaluation system.
+The evaluation system suggests three translators and the annotators rate them by comparing between their factors.
 In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture.
-Applied learning to rank methods and results are described in Section \ref{sec:methods}.
-\textit{Proficiency Estimator} stores the previous-translated documents in the cloud and indexes them using Lucene library.
-The similarity between query and indexed documents is used as a base for estimation of translator's proficiency.
-In order to find proficiency value, the similarity scores are aggregated.
+Applied learning to rank methods and results are described in Section \ref{sec:apply}.
+The \textit{Proficiency Estimator} system stores the previous-translated documents in the cloud and indexes them using Lucene library.
+The similarity between query and indexed documents is used as a basis for estimation of translator's proficiency.
+In order to find proficiency value, the platform aggregates the similarity scores.
 The applied aggregation function is described in Section \ref{sec:apply}.
-\textit{Scheduler} system figures out the delivery time based on timetable of translators.
-The scheduler builds a special data structure to calculate the response time.
+The \textit{Scheduler} system figures out the delivery time based on timetable of translators.
+The scheduler builds a special data structure to calculate the delivery time in a reasonable response time.
 The detail of the process is out of scope of the paper.
-At last, \textit{Profiler} accumulates personal information, translators' preferences as well as offered price and translation duration per word.
 
-Beside translator, a proofreader selected by the client revises the final translation.
+Beside the translator, a proofreader selected by the client revises the final translation.
 As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).
 The assessment is defined as a value between $1$ (very bad) and $5$ (perfect).
-As it is discussed in Section \ref{sec:apply}, it is used to evaluate aggregation algorithms for translator's proficiency.
+As it is discussed in Section \ref{sec:apply}, it is used to evaluate and compare aggregation algorithms for translator's proficiency.

### 2014-02-25 docs/seminar/evaluation.tex
revising

--- 2014-02-18 docs/seminar/evaluation.tex
@@
 Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using $181$ records of purchased orders.
-Table \ref{table:signtest} represents the Significance Test of both methods calculated by R.
+In addition it represents the Significance Test of both methods calculated by R.
 
@@
 The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
-Regarding to P-Value of significance test shown in Table \ref{table:signtest}, a meaningful relation between GP2 and feedbacks can be considered.
+Regarding to P-Value of significance test shown in Table \ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered.
 Top1 which has the worst values in the table shows a meaningless and near random correlation though.
@@
 \begin{table}
-\begin{center}
-\scalebox{1.2}{
-\begin{tabular}{p{1cm}|c|c|c|}
-\cline{2-4} & Top1 & Top5 & GP2  \\
-\hline \multicolumn{1}{ |c| }{$r_s$} & 0.052 & 0.089 & 0.145\\
-\hline \multicolumn{1}{ |c| }{$\tau$} & 0.034 & 0.059 & 0.102\\
+\begin{center}{
+\begin{tabular}{c c|c|c|c|}
+\cline{3-5} & & Top1 & Top5 & GP2  \\
+\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
+\cline{2-5} \multicolumn{1}{ |c| }{} & P-Value & 0.4866 & 0.2295 & 0.05038\\
+\hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
+\cline{2-5} \multicolumn{1}{ |c| }{} & P-Value & 0.5157 & 0.2562 & 0.05263\\
 \hline
@@
 }
-\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks}
+\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
 \label{table:correlation}
@@
 
+\subsection{Learning To Rank}
+In order to accumulate data required for ranking model, we conduct a survey filled by eight human annotators.
+The questions of survey represent three translators each with four criteria (price, delivery time, proficiency and number of cooperation times).
+The annotators rate the questions from one to three based on \textit{Total Order} strategy.
+The accumulated data consists of $400$ annotated list and overall $1200$ records.
+
+We use RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods.
+The library provides the  implementation of some Learning to Rank algorithms as well as evaluation measures in Java.
+By splitting the data in train, validation and test datasets, we use 5-Fold Cross-Validation on each run.
+One pointwise, three pairwise and two listwise methods are applied.
+
+Since evaluation of the results should be applied on whole the result list (with $3$ items), we have to use relevance grading evaluation measures like DCG, NDCG or ERR.
+In the current study, NDGC and ERR both with rank position at $3$ are used.
+
+Concerning the short final predicted list ($3$ items), every evaluator measure returns high result value even for a random ranker.
+This issue urges the need to run the evaluation on random data in order to find a baseline for comparison.
+We tackle the problem with two approaches.
+In the first approach, we run all the algorithms on data with random generated labels.
+In order to increase the accuracy of results, the process of generating randomized label is repeated $5$ times.
+The second approach is developing a simple ranker which randomly predicts the rank of each record.
+
+The result is shown in Table \ref{table:l2rresult}.
+Figure \ref{fig:l2rdiagram} depicts the corresponding data in diagrams.
+As it is shown, random values define a base line for comparison the goodness of methods.
+Among the applied methods, Linear Regression and LambdaMART tend to have better results.
+Furthermore, tracing NDCG and ERR diagrams shows a considerable similarity in behavior of both evaluation methods regarding to the data.
+
+In addition to comparing the methods, features comparison can be an interesting point.
+Table \ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model.
+The coefficient value is a measure for understanding the importance of each feature in comparison to the others.
+As it is shown, price and delivery time seem to be the most effective features while the number of cooperation times has the lowest importance.
+
 \begin{table}
-\begin{center}
-\scalebox{1.2}{
-\begin{tabular}{p{1cm}|c|c|c|}
-\cline{2-4} & Top1 & Top5 & GP2  \\
-\hline \multicolumn{1}{ |c| }{$r_s$} & 0.4866 & 0.2295 & 0.05038\\
-\hline \multicolumn{1}{ |c| }{$\tau$} & 0.5157 & 0.2562 & 0.05263\\
+\begin{center}{
+\begin{tabular}{|c|c|c|c|c|}
+\hline \multirow{2}{*}{Method} & \multicolumn{2}{ c| }{NDCG@3} & \multicolumn{2}{ c| }{ERR@3}  \\
+\cline{2-5} & Result & Random & Result & Random \\
+\hline Linear Regression & \textbf{0.935} & 0.833 & \textbf{0.451} & 0.375 \\
+\hline RankNet & 0.876 & 0.834 & 0.394 & 0.378 \\
+\hline RankBoost & 0.909 & 0.831 & 0.432 & 0.374 \\
+\hline LambdaMART & 0.93 & 0.832 & 0.447 & 0.373 \\
+\hline ListNet & 0.915 & 0.831 & 0.439 & 0.375 \\
+\hline AdaRank & 0.857 & 0.83 & 0.399 & 0.373 \\
+\hline Random Ranker & 0.832 & 0.832 & 0.375 & 0.378 \\
 \hline
@@
 }
-\caption{P-Value of Significance of Correlation Test Algorithms}
-\label{table:signtest}
+\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
+\label{table:l2rresult}
 \end{center}
@@
 
-\subsection{Learning To Rank}
-TODO
+\begin{figure}[h]
+\begin{center}
+\includegraphics[scale=0.5]{figures/l2rdiagram.png}
+\caption{Learning to Rank Results
+\label{fig:l2rdiagram}}
+\end{center}
+\end{figure}
+
+\begin{table}
+\begin{center}{
+\begin{tabular}{|c|c|}
+\hline Feature & Value  \\
+\hline Price & 2.002 \\
+\hline Duration & 0.057 \\
+\hline Proficiency & -0.048 \\
+\hline Number of Cooperation Times & -0.313 \\
+\hline
+\end{tabular}
+}
+\caption{Coefficient value of features in Linear Regression model}
+\label{table:l2rcoefficient}
+\end{center}
+\end{table}

### 2014-02-25 docs/seminar/methods.tex
revising

@@
 \begin{align*}
-GP2 = \frac{\sqrt{\sqrt{2/{no\_docs_x}_i}}/(\sqrt{(10/R)+R}}{\sqrt{sq(10/R)+R+sq(10/R)+\sqrt{R*2}}}
+GP2 = \frac{\sqrt{\sqrt{2/{no\_docs_x}_i}}/(\sqrt{(10/R)+R})}{\sqrt{sq(10/R)+R+sq(10/R)+\sqrt{R*2}}}
 \end{align*}
@@
 
-One primitive step in accumulating data required for learning to rank, is relevance judgment done by human annotators. \citet{l2r-book} introduces three main strategies as follows.
+One primitive step in accumulating data required for learning to rank, is relevance judgment normally done by human annotators. \citet{l2r-book} introduces three main strategies as follows.
 \begin{itemize}
-\item \textit{Relevance degree}: It specifies whether an object is relevant or not to the query.
+\item \textit{Relevance degree}: In this method, the annotator specifies whether an object is relevant or not to the query.
 It can be either in binary judgment or by specifying the degree of relevance (e.g., Perfect, Excellent, Good, Fair, or Bad).
-\item \textit{Pairwise preference}: A pair of objects are compared in order to specify which one is more relevant with regards to a query.
-\item \textit{Total order}: The total order of all object with respect to a query is specified.
+\item \textit{Pairwise preference}: The annotator compares a pair of objects in order to specify which one is more relevant with regards to a query.
+\item \textit{Total order}: The annotator specifies the total order of all objects with respect to a query by rating each object.
 \end{itemize}
 
-Among the three mentioned kinds of judgments, since the first is the easiest to obtain, it is the most popularly used judgment. While the third kind is more accurate but tedious for human annotators.
+Among the three mentioned kinds of judgments, the first one is the most popularly used judgment since is the easiest to obtain. While the third one is more accurate but laborious for human annotators.
 
@@
 Therefore, the group structure of ranking is ignored in this approach \citep{l2r-intro}.
+Linear or polynomial regression are widely used methods regarding to the approach.
 
@@
 In fact, it cares about the relative order between two documents.
-In the pairwise approach, the group structure of ranking is also ignored \citep{l2r-intro}.
-Here is a brief explanation of some of widely used pairwise algorithms:
+Similar to the pointwise, the pairwise approach also ignores the group structure of ranking\citep{l2r-intro}.
+Here is a brief explanation of some pairwise algorithms:
 
@@
 \item \textit{RankNet} \citep{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
-\item \textit{RankBoost} \citep{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over document pairs.
+\item \textit{RankBoost} \citep{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.
 \item \textit{LambdaRank} \citep{l2r-lambdarank}: It considers the evaluation measures to set its pair weight.
 In particular, the evaluation measures (which are position based) are directly used to define the gradient with respect to each document pair in the training process.
-\item \textit{LambdaMART} \citep{l2r-lambdamart}: It combines the strengths of boosted tree classification and \textit{LambdaRank}.
+\item \textit{LambdaMART} \citep{l2r-lambdamart}: It combines the strengths of boosted tree classification and LambdaRank.
 \end{itemize}
@@
 The listwise approach takes the entire set of documents associated with a query in the training data as the input and predicts their ground truth labels \citep{l2r-book}.
-The group structure of ranking is maintained and
-ranking evaluation measures can be more directly incorporated into the loss functions in learning \citep{l2r-intro}. In the following, two common listwise algorithms are briefly discussed:
+In contradiction to two previous approaches, it maintains the group structure of ranking.
+In addition, ranking evaluation measures can be more directly incorporated into the loss functions in learning \citep{l2r-intro}.
+In the following, two common listwise algorithms are briefly discussed:
 
@@
 
-As the different data-set are compared in \citet{l2r-book}, listwise techniques are in general the most effective among the others.
+\citet{l2r-book} compares the algorithms by applying on different data-sets.
+It concludes that listwise techniques are in general the most effective among the others.
 However, the choice of the learning evaluation measure and the rank cutoff may have a noticeable impact on the effectiveness of the learned model \citep{l2r-when}.
 
-A highly important point in all kinds of information retrieval systems is evaluation of results.
-The evaluation on the performance of a ranking model is carried out by comparison between the ranking lists output by the model and the ranking lists given as the ground truth \citep{l2r-intro}.Some common IR evaluation methods like Mean average precision (MAP), [Normalized] Discounted Cumulative Gain ([N]DCG), Mean Reciprocal Rank (MRR) are also widely user in leaning to rank evaluation.
+A critical point in all kinds of information retrieval systems is evaluation of results.
+The evaluation on the performance of a ranking model is carried out by comparison between the ranking lists output of the model and the ranking lists given as the ground truth.
+Some common IR evaluation methods like Mean average precision (MAP), [Normalized] Discounted Cumulative Gain ([N]DCG), Mean Reciprocal Rank (MRR) are also widely user in leaning to rank evaluation.
 Among the mentioned metrics, DCG/NDCG is the only one used for graded relevance.

### 2014-02-25 docs/seminar/conclusion.tex
writing conclusion

\section{Conclusion and Future Work}
\label{sec:conclusion}
In the paper, we put forward a comprehensive solution for implementation and design of a translator-expert retrieval system. As well as system architecture, we thoroughly study the obstacles and pitfalls in implementation of such a system. Document aggregation as well as ranking problems are two main issues thoroughly discussed in the paper and followed by provided solutions.

The first issue concerns with the comparison of the aggregation methods. The aggregation methods estimate the proficiency of each translator based on the similarity values of the previous translated documents with the query document. Using the assessment of the proof-readers on the final translation as the golden data, we compare three aggregation methods. Finally, GP2 method shows better performance in comparison to the others with reasonable good results.

The second issue tackles the problem of experts ranking. By applying different learning to rank algorithms, we obtain a ranking model based on linear regression with fairly good performance. The model's performance is approved by both NDCG and ERR evaluation measures. Feature analysis of data indicates the importance of price and delivery time in comparison to the other features for the the human annotators.

Recently, different aspects of expert retrieval platforms drawing an increasing interest. Based on the current study, we aim to accomplish a comprehensive aggregation method regarding to the translation context in the following studies.

### 2014-03-08 docs/seminar/casestudy.tex
revising

@@
 \label{sec:casestudy}
-The data flow of expert searching is depicted in Figure\ref{fig:architecture}.
+The data flow of expert searching is depicted in Figure \ref{fig:architecture}.
 The client submits a document and searches for translators with a specific target language.
-Based on query document, the framework figures out offered price, delivery time, proficiency of translators and number of cooperation times related to each translator.
+Based on the query document, the framework figures out the offered price, delivery time, proficiency of translators as well as the number of cooperation times related to each translator.
 The ranking system processes the calculated values and the offers the most related translators to the client.
@@
 
-The \textit{Profiler} is responsible for accumulating personal information, translators' preferences, offered price and translation duration per word.
+The \textit{Profiler} is responsible for accumulating translators' professional information,  offered price and translation duration per word.
 The \textit{Ranking} system uses Learning to Rank techniques to return the most related translators to the client.
-The training data is provided by a group of annotators who are familiar with business of company using an evaluation system.
+The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system.
 The evaluation system suggests three translators and the annotators rate them by comparing between their factors.
@@
 Applied learning to rank methods and results are described in Section \ref{sec:apply}.
-The \textit{Proficiency Estimator} system stores the previous-translated documents in the cloud and indexes them using Lucene library.
-The similarity between query and indexed documents is used as a basis for estimation of translator's proficiency.
-In order to find proficiency value, the platform aggregates the similarity scores.
+The \textit{Proficiency Estimator} system stores the previous-translated documents in the cloud and indexes them using Lucene.
+The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency.
+The proficiency value is compared by aggregating the similarity scores.
 The applied aggregation function is described in Section \ref{sec:apply}.
@@
 The scheduler builds a special data structure to calculate the delivery time in a reasonable response time.
-The detail of the process is out of scope of the paper.
+The details of the process are out of scope of the paper.
 
@@
 The assessment is defined as a value between $1$ (very bad) and $5$ (perfect).
-As it is discussed in Section \ref{sec:apply}, it is used to evaluate and compare aggregation algorithms for translator's proficiency.
+We use these assessments to evaluate and compare aggregation algorithms for translator's proficiency.

### 2014-03-08 docs/seminar/evaluation.tex
revising

@@
 
+By calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field.
+In the next step, in order to compare the algorithms, we test the correlation of each list with the proof-readers' feedbacks.
+
 In order to calculate the correlation value, we applied Spearman Rank Order and Kendall Rank Correlation as two common methods.
 Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using $181$ records of purchased orders.
-In addition it represents the Significance Test of both methods calculated by R.
+In addition, it represents the Significance Test of both methods.
+For Spearman's test, p-values are computed using algorithm AS 89 \citep{as89}.
 
@@
 
-We use RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods.
+We use the RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods.
 The library provides the  implementation of some Learning to Rank algorithms as well as evaluation measures in Java.
@@
 
-Concerning the short final predicted list ($3$ items), every evaluator measure returns high result value even for a random ranker.
+Because of the short final predicted list ($3$ items), every evaluator measure returns high result value even for a random ranker.
 This issue urges the need to run the evaluation on random data in order to find a baseline for comparison.
@@
 The second approach is developing a simple ranker which randomly predicts the rank of each record.
+In fact, the first tests whether there is anything to learn in the data and the second examines if the learning algorithms learn from the data.
 
@@
 The coefficient value is a measure for understanding the importance of each feature in comparison to the others.
+
 As it is shown, price and delivery time seem to be the most effective features while the number of cooperation times has the lowest importance.
+Surprisingly, proficiency plays a small role in the ranking of the translators.
+It can be because of the proposed business plan of the platform to the clients which guarantees an acceptable quality of translation.
+In addition, we expect that by applying the methods on much more amount of data, the proficiency feature gains more importance.
 

### 2014-03-08 docs/seminar/introduction.tex
revising

@@
 
-With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR and not just traditional document retrieval, such as entity retrieval and expertise retrieval \citep{er-sparse}.
+With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}  and not just traditional document retrieval.
 The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.
@@
 
-Ranking techniques are mostly one of the essential parts of IR frameworks.
-In recent years, Learning to Rank (L2R) has been studied extensively specially for document retrieval.
+Ranking techniques are an essential part of each IR framework.
+In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval.
 It refers to machine learning techniques for training the model in a ranking task \citep{er}.
@@
 
-As well as ranking techniques, aggregation functions have a significant effect on the performance of IR systems. Aggregate tasks are those where documents' similarities are not
+As well as ranking techniques, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
 the final outcome, but instead an intermediary component.
@@
 This paper addresses the problem of searching translators as experts.
+We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform.
+In contrast to common expert retrieval systems, we include significant factors of searching a translator (like price and delivery time) in the study as well as the relevance of the documents to the query document.
 We have applied Learning to Rank in a candidate-based approach.

### 2014-03-08 docs/seminar/methods.tex
revising

@@
-\section{Methods}
+\section{Methods and Related Work}
 \label{sec:methods}
@@
 
-The effect of different features on aggregation function is studied in \citet{agg-gp2}.
-As it is shown, number of documents is tightly related such that the performance of different queries are optimal for different values of $N$.
-Comparing query-based features using statistical measures, it inferred that the features may not, in general, be able to predict the optimal number of documents to aggregate for each query.
-Individual Expert Features is discussed in the next step.
-It is shown that relevant experts are associated with a higher ranked document than non-relevant experts.
+The effect of different features on the aggregation function is studied in \citet{agg-gp2}.
+They show that the number of documents is an important factor, such that the performance of different queries are optimal for different values of $N$.
+Comparing query-based features using statistical measures, they infer that the document features (such as TF, IDF) may not, in general, be able to predict the optimal number of documents to aggregate for each query.
+In contrast, individual Expert Features have been shown to be more informative such that relevant experts are associated with a higher ranked document than non-relevant experts.
 More interestingly, relevant experts are associated with less documents on average.
@@
 \citet{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise.
-Eleven data fusion as well as three statistically different document weighting were tested.
-In practice, the approach considers both number of documents and expert features regarding to the ranking score of the documents.
-The results show that while some of adapted voting techniques are most likely outperform others, the proposed approach is effective when using appropriate one.
+Eleven data fusion methods as well as three statistically different document weighting models were tested.
+In practice, the approach considers both the number of documents and expert features regarding to the ranking score of the documents.
+The results show that while some of adapted voting techniques most likely outperform others, the proposed approach is effective when using the appropriate one.
 
@@
 Learning to rank refers to machine learning techniques for training the model in a ranking task.
-Due to its importance, learning to rank has been drawing broad attention in the machine learning community recently.
+Due to importance of ranking problems, learning to rank has been drawing broad attention in the machine learning community recently.
 
-In learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied.
-As \citet{l2r-intro} points out the relation between learning to rank and ordinal classification, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
+In the learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied.
+As \citet{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
 
@@
 
-A critical point in all kinds of information retrieval systems is evaluation of results.
+A critical point in all kinds of information retrieval systems is the evaluation of results.
 The evaluation on the performance of a ranking model is carried out by comparison between the ranking lists output of the model and the ranking lists given as the ground truth.
@@
 In other words, it assumes that a user is more likely to stop browsing if they have already seen one or more highly relevant documents.
-By presenting ERR formula in \cite{l2r-err}, it claims that results reflects real user browsing behavior better and quantifies user satisfaction more accurately than DCG.
+Introducing the ERR formula, \cite{l2r-err} claim that results reflect real user browsing behavior better and quantifies user satisfaction more accurately than DCG.

### 2014-04-12 docs/seminar/casestudy.tex
paper draft

@@
 \label{sec:casestudy}
-The data flow of expert searching is depicted in Figure \ref{fig:architecture}.
-The client submits a document and searches for translators with a specific target language.
-Based on the query document, the framework figures out the offered price, delivery time, proficiency of translators as well as the number of cooperation times related to each translator.
-The ranking system processes the calculated values and the offers the most related translators to the client.
-
-As it is shown in Figure \ref{fig:architecture}, the essential components of the framework are \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiler}.
+Essential components of the platform as well as the work-flow of searching for the translators are depicted in Figure \ref{fig:architecture}.
+The platform consist of four main components: \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiles}.
 
@@
 \begin{center}
-\includegraphics[scale=0.8]{figures/dataflow.jpg}
-\caption{System Data Flow
+\includegraphics[scale=0.8]{figures/dataflow.png}
+\caption{Translator-Expert Search Work Flow
 \label{fig:architecture}}
@@
 
-The \textit{Profiler} is responsible for accumulating translators' professional information,  offered price and translation duration per word.
-The \textit{Ranking} system uses Learning to Rank techniques to return the most related translators to the client.
+The \textit{Profiles} stores translator profile information i.e.
+source and target languages, offered price and translation duration per word.
+The \textit{Scheduler} system figures out the delivery time based on timetable of translators.
+The scheduler builds an efficient data structure to calculate the delivery time in a reasonable response time.
+The details of the process are out of scope of the paper.
+The \textit{Proficiency Estimator} system stores the previous-translated documents and indexes them using Lucene.
+The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency.
+In fact, the proficiency value is achieved by aggregating the documents similarity scores.
+The applied aggregation function is described in Section\ref{sec:apply}.
+At last, the \textit{Ranking} system uses all the data provided in the previous steps to create the ranking model.
+The \textit{Ranking} system applies Learning to Rank techniques to return the most related translators to the client.
 The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system.
@@
 In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture.
-Applied learning to rank methods and results are described in Section \ref{sec:apply}.
-The \textit{Proficiency Estimator} system stores the previous-translated documents in the cloud and indexes them using Lucene.
-The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency.
-The proficiency value is compared by aggregating the similarity scores.
-The applied aggregation function is described in Section \ref{sec:apply}.
-The \textit{Scheduler} system figures out the delivery time based on timetable of translators.
-The scheduler builds a special data structure to calculate the delivery time in a reasonable response time.
-The details of the process are out of scope of the paper.
+Applied learning to rank methods and results are described in Section\ref{sec:apply}.
 
-Beside the translator, a proofreader selected by the client revises the final translation.
-As well as reviewing, the proofreader assesses the quality of translation from different points of view (grammar, style, accuracy, content and language).
-The assessment is defined as a value between $1$ (very bad) and $5$ (perfect).
-We use these assessments to evaluate and compare aggregation algorithms for translator's proficiency.
+The client submits a document and searches for translators with a specific target language.
+Based on the query document, the framework figures out the offered price, delivery time, proficiency of translators as well as the number of cooperation times related to each translator.
+The ranking system processes the calculated values and offers the most related translators to the client.
+
+Beside the mentioned work-flow after finishing the translation, another expert called proofreader revises the translation.
+The proofreader is selected by the client and guarantees the quality of the final translation.
+As well as revising, the proofreader assesses the quality of translator's task from different points of view (grammar, style, accuracy, content and language).
+The assessment value can be from $1$ (very bad) to $5$ (perfect).
+As it is described in Section\ref{sec:apply}, we use these assessments to evaluate and compare aggregation algorithms.

### 2014-04-12 docs/seminar/evaluation.tex
paper draft

@@
 \subsection{Aggregation Functions}
-In order to compare different aggregation functions, similar to \citet{agg-gp2} three algorithms are selected.
-$GP2$ as well as $Top1$ and $Top5$ which are two common forms of $TopN$ aggregation algorithm.
-$TopN$ refers to algorithm that summarizes the $N$ top documents (i.e.
+Translator's proficiency is one of the attributes used for creating the ranking model.
+In order to achieve the value, we aggregate the similarity values of the previous translated documents with the query document.
+Selecting the most appropriate aggregation function is the objective of the current section.
+
+Similar to \citet{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
+$Top1$ and $Top5$ are two common forms of $TopN$ aggregation algorithm which refers to algorithm that summarizes the $N$ top documents (i.e.
 $Top1$ only using the top associated document to rank the candidates).
 
-Feedbacks of proof-readers after every translation are used as a basis for evaluating the algorithms.
-Since feedbacks are a measure for quality of translation, the more similar the ranking of algorithms to feedbacks are the better it is.
+In order to evaluate aggregation functions results, we use the assessment of the proof-readers after every translation as the basis for the comparison.
+**the reason**.
+Therefore, the more similar the results of the algorithm to the assessments are the better the algorithm is.
 
 By calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field.
-In the next step, in order to compare the algorithms, we test the correlation of each list with the proof-readers' feedbacks.
+In the next step, in order to compare the algorithms, we test the correlation of each list with the list of translations annotated with proof-readers' assessments.
 
@@
 The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
-Regarding to P-Value of significance test shown in Table \ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered.
+Regarding to P-Value of significance test shown in Table\ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered.
 Top1 which has the worst values in the table shows a meaningless and near random correlation though.
@@
 The questions of survey represent three translators each with four criteria (price, delivery time, proficiency and number of cooperation times).
+As it is mentioned before, in order to prevent bias in results, the name and the picture of the translators are hidden from the annotators.
 The annotators rate the questions from one to three based on \textit{Total Order} strategy.
@@
 
-The result is shown in Table \ref{table:l2rresult}.
-Figure \ref{fig:l2rdiagram} depicts the corresponding data in diagrams.
+The result is shown in Table\ref{table:l2rresult}.
+Figure\ref{fig:l2rdiagram} depicts the corresponding data in diagrams.
 As it is shown, random values define a base line for comparison the goodness of methods.
@@
 In addition to comparing the methods, features comparison can be an interesting point.
-Table \ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model.
+Table\ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model.
 The coefficient value is a measure for understanding the importance of each feature in comparison to the others.

### 2014-04-12 docs/seminar/introduction.tex
paper draft

@@
 
-With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}  and not just traditional document retrieval.
-The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.
+With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}.
+The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.
 
-Two principal approaches are proposed by \citet{trec2005} based on probabilistic language modeling techniques.
-They were formalized as so-called candidate models and document models.
+\citet{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques.
+They were formalized as so-called \textit{candidate models} and \textit{document models}.
 The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query.
@@
 We have applied Learning to Rank in a candidate-based approach.
-Additionally, different aggregation algorithms related to documents of translators have been studied.
+Additionally, different aggregation algorithms related to documents of translators have been studied and compared.
 
 The remaining of the paper is organized as follows.
-In Section \ref{sec:casestudy}, the Translator-Expert Retrieval framework is described in detail.
-Then, Section \ref{sec:methods} explains methods used in the study.
-In Section \ref{sec:apply}, we report the result of applied methods on the framework.
-Finally, we conclude the study in Section \ref{sec:conclusion}.
+In Section\ref{sec:casestudy}, the Translator-Expert Retrieval framework is described in detail.
+Then, Section\ref{sec:methods} explains methods used in the study.
+In Section\ref{sec:apply}, we report the result of applied methods on the framework.
+Finally, we conclude the study in Section\ref{sec:conclusion}.

### 2014-04-14 docs/seminar/abstract.tex
revising seminar
changed abstract and others

@@
-Expertise Retrieval, whose task is to suggest people with relevant expertise regarding to a query, has received increasing interest in recent years.
-In this paper, we proposed an Expert Retrieval platform narrowed down to Translators as experts.
+%Expertise Retrieval, whose task is to suggest people with relevant expertise regarding to a query, has received increasing interest in recent years.
+In this paper, we propose an Expert Retrieval platform narrowed down to translators as experts.
 Issues and obstacles during design and development as well as acquired solutions and results are reported.
 Ranking the translators using Learning to Rank as well as documents' aggregation functions are two main issues which are specifically studied in the paper.
+
+This article describes a method and tool to identify expert translators in an online translation service.
+We start from existing efforts on expert retrieval and factor in additional parameters based on the real-world scenario of the task.
+The system first identifies topical expertise using an aggregation function over relevance scores of previously translated documents by each translator, and then a learning to rank method to factor in non-topical relevance factors that are part of the decision-making process of the user, such as price and duration of translation.
+We test the system on a manually created test collection and show that the method is able to effectively support the user in selecting the best translator.

### 2014-04-14 docs/seminar/evaluation.tex
changed abstract and others

@@
-\section{Apply The Methods and Results}
+\section{Experimental Results}
 \label{sec:apply}
@@
 
-Similar to \citet{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
+Similar to \cite{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
 $Top1$ and $Top5$ are two common forms of $TopN$ aggregation algorithm which refers to algorithm that summarizes the $N$ top documents (i.e.
@@
 In addition, it represents the Significance Test of both methods.
-For Spearman's test, p-values are computed using algorithm AS 89 \citep{as89}.
+For Spearman's test, p-values are computed using algorithm AS 89 \cite{as89}.
 
@@
 \begin{center}{
+\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
 \begin{tabular}{c c|c|c|c|}
@@
 \hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$r_s$}} & Correlation Test & 0.052 & 0.089 & 0.145\\
-\cline{2-5} \multicolumn{1}{ |c| }{} & P-Value & 0.4866 & 0.2295 & 0.05038\\
+\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.4866 & 0.2295 & 0.05038\\
 \hline \multicolumn{1}{ |c| }{\multirow{2}{*}{$\tau$}} & Correlation Test & 0.034 & 0.059 & 0.102\\
-\cline{2-5} \multicolumn{1}{ |c| }{} & P-Value & 0.5157 & 0.2562 & 0.05263\\
+\cline{2-5} \multicolumn{1}{ |c| }{} & p-Value & 0.5157 & 0.2562 & 0.05263\\
 \hline
@@
 }
-\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
 \label{table:correlation}
@@
 
-We use the RankLib library \footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods.
+We use the RankLib library\footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods.
 The library provides the  implementation of some Learning to Rank algorithms as well as evaluation measures in Java.
@@
 \begin{center}{
+\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
 \begin{tabular}{|c|c|c|c|c|}
@@
 }
-\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
 \label{table:l2rresult}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \begin{center}
@@
 \begin{center}{
+\caption{Coefficient value of features in Linear Regression model}
 \begin{tabular}{|c|c|}
@@
 }
-\caption{Coefficient value of features in Linear Regression model}
 \label{table:l2rcoefficient}

### 2014-04-14 docs/seminar/introduction.tex
changed abstract and others

@@
 The goal of expertise retrieval is to link humans to expertise areas, and vice versa.
-In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \citep{er, er-community-aware}.
+In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er,er-community-aware}.
 
-With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}.
-The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.
+With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval \cite{er-sparse}.
+The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005,er-community-aware}.
 
-\citet{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques.
+\cite{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques.
 They were formalized as so-called \textit{candidate models} and \textit{document models}.
 The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query.
-The document models first find documents relevant to the topic and then locate the experts associated with these documents \citep{er}.
+The document models first find documents relevant to the topic and then locate the experts associated with these documents \cite{er}.
 
@@
 In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval.
-It refers to machine learning techniques for training the model in a ranking task \citep{er}.
-In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \citep{l2r-intro}.
+It refers to machine learning techniques for training the model in a ranking task \cite{er}.
+In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \cite{l2r-intro}.
 
@@
 the final outcome, but instead an intermediary component.
-In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.
+In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \cite{agg-learning}.
 

### 2014-04-14 docs/seminar/methods.tex
changed abstract and others

@@
 
-The effect of different features on the aggregation function is studied in \citet{agg-gp2}.
+The effect of different features on the aggregation function is studied in \cite{agg-gp2}.
 They show that the number of documents is an important factor, such that the performance of different queries are optimal for different values of $N$.
@@
 
-\citet{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise.
+\cite{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise.
 Eleven data fusion methods as well as three statistically different document weighting models were tested.
@@
 
-Later on, focusing on related features discussed before \citet{agg-gp2} introduces a new aggregation method.
+Later on, focusing on related features discussed before \cite{agg-gp2} introduces a new aggregation method.
 It uses genetic programming to learn a formula for the weights of document associations within the candidate profiles.
@@
 In the learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied.
-As \citet{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
+As \cite{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
 
-One primitive step in accumulating data required for learning to rank, is relevance judgment normally done by human annotators. \citet{l2r-book} introduces three main strategies as follows.
+One primitive step in accumulating data required for learning to rank, is relevance judgment normally done by human annotators. \cite{l2r-book} introduces three main strategies as follows.
 \begin{itemize}
@@
 In the pointwise approach, the ranking problem is transformed to classification, regression or ordinal classification.
-Therefore, the group structure of ranking is ignored in this approach \citep{l2r-intro}.
+Therefore, the group structure of ranking is ignored in this approach \cite{l2r-intro}.
 Linear or polynomial regression are widely used methods regarding to the approach.
@@
 In fact, it cares about the relative order between two documents.
-Similar to the pointwise, the pairwise approach also ignores the group structure of ranking\citep{l2r-intro}.
+Similar to the pointwise, the pairwise approach also ignores the group structure of ranking\cite{l2r-intro}.
 Here is a brief explanation of some pairwise algorithms:
@@
 \begin{itemize}
-\item \textit{RankNet} \citep{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
-\item \textit{RankBoost} \citep{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.
-\item \textit{LambdaRank} \citep{l2r-lambdarank}: It considers the evaluation measures to set its pair weight.
+\item \textit{RankNet} \cite{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
+\item \textit{RankBoost} \cite{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.
+\item \textit{LambdaRank} \cite{l2r-lambdarank}: It considers the evaluation measures to set its pair weight.
 In particular, the evaluation measures (which are position based) are directly used to define the gradient with respect to each document pair in the training process.
-\item \textit{LambdaMART} \citep{l2r-lambdamart}: It combines the strengths of boosted tree classification and LambdaRank.
+\item \textit{LambdaMART} \cite{l2r-lambdamart}: It combines the strengths of boosted tree classification and LambdaRank.
 \end{itemize}
 
-The listwise approach takes the entire set of documents associated with a query in the training data as the input and predicts their ground truth labels \citep{l2r-book}.
+The listwise approach takes the entire set of documents associated with a query in the training data as the input and predicts their ground truth labels \cite{l2r-book}.
 In contradiction to two previous approaches, it maintains the group structure of ranking.
-In addition, ranking evaluation measures can be more directly incorporated into the loss functions in learning \citep{l2r-intro}.
+In addition, ranking evaluation measures can be more directly incorporated into the loss functions in learning \cite{l2r-intro}.
 In the following, two common listwise algorithms are briefly discussed:
@@
 \begin{itemize}
-\item \textit{AdaRank} \citep{l2r-adarank}: It applies the evaluation measures on the framework of Boosting and focuses on effectively optimization.
-\item \textit{ListNet} \citep{l2r-listnet}: It uses different probability distributions in order to define the loss function.
+\item \textit{AdaRank} \cite{l2r-adarank}: It applies the evaluation measures on the framework of Boosting and focuses on effectively optimization.
+\item \textit{ListNet} \cite{l2r-listnet}: It uses different probability distributions in order to define the loss function.
 \end{itemize}
 
-\citet{l2r-book} compares the algorithms by applying on different data-sets.
+\cite{l2r-book} compares the algorithms by applying on different data-sets.
 It concludes that listwise techniques are in general the most effective among the others.
-However, the choice of the learning evaluation measure and the rank cutoff may have a noticeable impact on the effectiveness of the learned model \citep{l2r-when}.
+However, the choice of the learning evaluation measure and the rank cutoff may have a noticeable impact on the effectiveness of the learned model \cite{l2r-when}.
 
@@
 
-Recently, \citet{l2r-err} have proposed a new evaluation metrics called Expected Reciprocal Rank (ERR) which claims to model user's satisfaction with search results better than the DCG metric.
-\citet{l2r-err} addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it.
-It asserts that based on research on modeling user click behavior \citep{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list.
+Recently, \cite{l2r-err} have proposed a new evaluation metrics called Expected Reciprocal Rank (ERR) which claims to model user's satisfaction with search results better than the DCG metric.
+\cite{l2r-err} addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it.
+It asserts that based on research on modeling user click behavior \cite{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list.
 In other words, it assumes that a user is more likely to stop browsing if they have already seen one or more highly relevant documents.

### 2014-04-15 docs/seminar/casestudy.tex
changed abstract and others
changed the intro and the case study section, as well as part of the methods

@@
-\section{Case Study}
+\section{Translator recommendation}
 \label{sec:casestudy}
+\subsection{Use-case}\label{sec:usecase}
+The user model for this application is that of an online user in possession of a document in a language other than the desired one.
+The need for a different language comes either from an internal need to know the contents of the document, or from an external requirement to provide the document in a high-quality translation in the desired language.
+However, the document is not simply an official document (e.g.
+a birth certificate) since the platform does not provide legal translation services.
+Therefore, we can assume that the document to be translated has a particular narrative and a certain topic.
+
+The task of this user is to identify a translator who balances translation quality with non-functional requirements such as cost and delivery time.
+
+The system is therefore charged to estimate the proficiency of the translator on the topic of the document at hand by considering previously translated documents, and to learn a preference model that a typical user will have in combining this proficiency estimation with the other aspects involved in the decision making process (monetary, temporal and social).
+A reasonable hypothesis, which we will verify in what follows, is that a high-proficiency, low-cost, fast-delivery, professionally known translator will be preferred.
+
+\subsection{The Platform}\label{sec:platform}
 Essential components of the platform as well as the work-flow of searching for the translators are depicted in Figure \ref{fig:architecture}.
@@
 
-\begin{figure*}[h]
+\begin{figure*}
 \begin{center}
-\includegraphics[scale=0.8]{figures/dataflow.png}
+\includegraphics[width=12cm]{figures/dataflow.png}
 \caption{Translator-Expert Search Work Flow
@@
 The \textit{Profiles} stores translator profile information i.e.
-source and target languages, offered price and translation duration per word.
+source and target languages, offered price and translation duration per word, and the number of translations the translator has performed for the same client.
 The \textit{Scheduler} system figures out the delivery time based on timetable of translators.
@@
 The details of the process are out of scope of the paper.
-The \textit{Proficiency Estimator} system stores the previous-translated documents and indexes them using Lucene.
+The \textit{Proficiency Estimator} system stores the previously-translated documents and indexes them using Lucene.
 The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency.
@@
 
-Beside the mentioned work-flow after finishing the translation, another expert called proofreader revises the translation.
+Separately from the mentioned workflow, after finishing the translation, another expert (a  proofreader) revises the translation.
 The proofreader is selected by the client and guarantees the quality of the final translation.
@@
 The assessment value can be from $1$ (very bad) to $5$ (perfect).
-As it is described in Section\ref{sec:apply}, we use these assessments to evaluate and compare aggregation algorithms.
+In Section\ref{sec:apply} we use these assessments to evaluate and compare aggregation algorithms.

### 2014-04-15 docs/seminar/introduction.tex
changed the intro and the case study section, as well as part of the methods

--- 2014-03-08 docs/seminar/introduction.tex
@@
 \label{sec:introduction}
-The goal of expertise retrieval is to link humans to expertise areas, and vice versa.
-In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \citep{er, er-community-aware}.
-
-With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}  and not just traditional document retrieval.
-The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.
-
-Two principal approaches are proposed by \citet{trec2005} based on probabilistic language modeling techniques.
-They were formalized as so-called candidate models and document models.
-The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query.
-The document models first find documents relevant to the topic and then locate the experts associated with these documents \citep{er}.
-
-Ranking techniques are an essential part of each IR framework.
-In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval.
-It refers to machine learning techniques for training the model in a ranking task \citep{er}.
-In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \citep{l2r-intro}.
-
-As well as ranking techniques, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
-the final outcome, but instead an intermediary component.
-In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.
+We look at the technology of Information Retrieval from the perspective of a real-world user scenario involving the selection of human translators based on a combination of expertise and practical factors.
+It has become more and more common place to consider search technology in a series of applications previously served only by database technology, if at all by a computer system~\cite{Grefenstette:2011}.
+In such cases, new data, new users, and new scenarios need to be observed, existing methods have to be adapted to the task at hand, and new evaluation procedures have to be devised.
 
@@
 We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform.
-In contrast to common expert retrieval systems, we include significant factors of searching a translator (like price and delivery time) in the study as well as the relevance of the documents to the query document.
-We have applied Learning to Rank in a candidate-based approach.
-Additionally, different aggregation algorithms related to documents of translators have been studied.
+In contrast to common expert retrieval systems, we include significant factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
+The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{http://github/anonymized}}.
 
 The remaining of the paper is organized as follows.
-In Section \ref{sec:casestudy}, the Translator-Expert Retrieval framework is described in detail.
-Then, Section \ref{sec:methods} explains methods used in the study.
-In Section \ref{sec:apply}, we report the result of applied methods on the framework.
-Finally, we conclude the study in Section \ref{sec:conclusion}.
+In Section\ref{sec:casestudy}, the use-case is presented and the Translator-Expert Retrieval framework is described in detail.
+Then, Section\ref{sec:methods} explains the methods used in the study.
+Section\ref{sec:apply} shows the result of applied methods on the framework.
+We discuss these results and conclude the study in Section\ref{sec:conclusion}.

### 2014-04-15 docs/seminar/methods.tex
changed the intro and the case study section, as well as part of the methods

@@
 \label{sec:methods}
-In this section, we study different methods and algorithms regarding to Aggregation Functions and Learning to Rank.
+With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval \cite{er-sparse}.
+The goal of expertise retrieval is to link humans to expertise areas, and vice versa.
+In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er,er-community-aware}.
+The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005,er-community-aware}.
 
+\cite{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques.
+They were formalized as so-called \textit{candidate models} and \textit{document models}.
+The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query.
+The document models first find documents relevant to the topic and then locate the experts associated with these documents \cite{er}.
+
+Ranking techniques are an essential part of each IR framework.
+In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval.
+It refers to machine learning techniques for training the model in a ranking task \cite{er}.
+In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \cite{l2r-intro}.
+
+As well as ranking techniques, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
+the final outcome, but instead an intermediary component.
+In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \cite{agg-learning}.
 \subsection{Aggregation Functions}

### 2014-04-17 docs/seminar/casestudy.tex
more changes to all sections

@@
 \subsection{The Platform}\label{sec:platform}
-Essential components of the platform as well as the work-flow of searching for the translators are depicted in Figure \ref{fig:architecture}.
-The platform consist of four main components: \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiles}.
+Essential components of the platform as well as the workflow of searching for the translators are depicted in Figure \ref{fig:architecture}.
+The platform consists of four main components: \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiles}.
 
@@
 \includegraphics[width=12cm]{figures/dataflow.png}
-\caption{Translator-Expert Search Work Flow
+\caption{Translator-Expert Search Workflow
 \label{fig:architecture}}
@@
 
-The \textit{Profiles} stores translator profile information i.e.
-source and target languages, offered price and translation duration per word, and the number of translations the translator has performed for the same client.
-The \textit{Scheduler} system figures out the delivery time based on timetable of translators.
+The \textit{Profiles} component stores translator profile information i.e.
+source and target languages, offered price and translation duration per word, as well as the number of translations the translator has performed for the same client.
+The \textit{Scheduler} system calculates the delivery time based on the timetable of each translator.
 The scheduler builds an efficient data structure to calculate the delivery time in a reasonable response time.
 The details of the process are out of scope of the paper.
-The \textit{Proficiency Estimator} system stores the previously-translated documents and indexes them using Lucene.
-The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency.
-In fact, the proficiency value is achieved by aggregating the documents similarity scores.
-The applied aggregation function is described in Section\ref{sec:apply}.
-At last, the \textit{Ranking} system uses all the data provided in the previous steps to create the ranking model.
-The \textit{Ranking} system applies Learning to Rank techniques to return the most related translators to the client.
-The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system.
-The evaluation system suggests three translators and the annotators rate them by comparing between their factors.
+In this report we focus on the Proficiency Estimator and the Ranking elements.
+
+The \textit{Proficiency Estimator} sub-system stores the previously-translated documents of each translator and indexes them using Lucene.
+The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency for the task at hand.
+The proficiency score is obtained by aggregating the documents' similarity scores.
+Different aggregation functions are analyzed in Section\ref{sec:apply}.
+Finally, the \textit{Ranking} sub-system uses all the data generated in the previous steps to create the ranking model.
+It uses Learning to Rank techniques to return the most relevant candidate translators.
+The training data is provided by a group of annotators  familiar with the business of the company, using an evaluation system created specifically for this generating this ground truth.
+The evaluation system presents three translators and the annotators rank them based on the values of each of their attributes (i.e.
+proficiency, delivery time, price, cooperation).
 In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture.
-Applied learning to rank methods and results are described in Section\ref{sec:apply}.
+The applied learning to rank methods and their results are described in Section\ref{sec:apply}.
 
-The client submits a document and searches for translators with a specific target language.
+%The client submits a document and searches for translators with a specific target language.
 Based on the query document, the framework figures out the offered price, delivery time, proficiency of translators as well as the number of cooperation times related to each translator.

### 2014-04-17 docs/seminar/evaluation.tex
more changes to all sections

@@
 \label{sec:apply}
-In this section, we applied different approaches on the platform. By comparing the methods, we aim to discover the most appropriate one regarding to the project's characteristics and data.
+In this section, we applied the different approaches presented in the previous section within our platform.
+By comparing the methods, we aim to discover the most appropriate one considering to the project's characteristics and data.
 
 \subsection{Aggregation Functions}
-Translator's proficiency is one of the attributes used for creating the ranking model.
-In order to achieve the value, we aggregate the similarity values of the previous translated documents with the query document.
+Translator's proficiency on the topic of the query is one of the attributes used for creating the ranking model.
+In order to obtain the value, we aggregate the similarity values of the previously translated documents with the query document.
 Selecting the most appropriate aggregation function is the objective of the current section.
 
+In order to evaluate aggregation functions results, we use the assessment of the proof-readers after every translation.
+As mentioned before, the hypothesis is that a translator is likely to do a better job if she is familiar with the vocabulary of the query.
+We can then use the proof-readers assessments as a gold standard and observe which of the three aggregation methods correlates more with the scores given by the proof-readers.
+
 Similar to \cite{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
-$Top1$ and $Top5$ are two common forms of $TopN$ aggregation algorithm which refers to algorithm that summarizes the $N$ top documents (i.e.
-$Top1$ only using the top associated document to rank the candidates).
+$GP2$ is the state of the art, while $Top1$ and $Top5$ are two common forms of $TopN$ aggregation algorithm which refers to algorithm that summarizes the $N$ top documents.
+Furthermore, $Top1$ can be interpreted as the maximum similarity score, and follows the intuition that it is sufficient for a translator to have had only one highly similar translation job before in order to do a good job on the new task.
 
-In order to evaluate aggregation functions results, we use the assessment of the proof-readers after every translation as the basis for the comparison.
-**the reason**.
-Therefore, the more similar the results of the algorithm to the assessments are the better the algorithm is.
+As input data we have 181 translation orders collected from the live system.
+For each of them, we know the translator who performed the translation (including all her previously translated documents), the text of the document to be translated, and the score given by the proof-reader.
+Because this is historical data, evaluating the aggregation method cannot be done by giving the same translation task to different translators.
+However, vy calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field.
+Then, in order to compare the algorithms, we test the correlation of each list with the list of translations annotated with proof-readers' assessments.
+Again, the assumption being that if we rank translation jobs by aggregation scores, the top elements would have high proof-reader scores, while the bottom elements lower scores.
 
-By calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field.
-In the next step, in order to compare the algorithms, we test the correlation of each list with the list of translations annotated with proof-readers' assessments.
+%mihai: put a plot here. On the X-axis the proof-reader scores and on the Y-axis the aggregation scores.
 
 In order to calculate the correlation value, we applied Spearman Rank Order and Kendall Rank Correlation as two common methods.
-Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using $181$ records of purchased orders.
+Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using the 181 records of purchased orders.
 In addition, it represents the Significance Test of both methods.
@@
 The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
-Regarding to P-Value of significance test shown in Table\ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered.
+Regarding to p-Value of significance test shown in Table\ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered.
 Top1 which has the worst values in the table shows a meaningless and near random correlation though.
@@
 \subsection{Learning To Rank}
-In order to accumulate data required for ranking model, we conduct a survey filled by eight human annotators.
+In order to accumulate data required for ranking model, we conduct a survey with eight human annotators.
 The questions of survey represent three translators each with four criteria (price, delivery time, proficiency and number of cooperation times).
-As it is mentioned before, in order to prevent bias in results, the name and the picture of the translators are hidden from the annotators.
+As mentioned before, in order to prevent bias in results, the name and the picture of the translators are hidden from the annotators.
 The annotators rate the questions from one to three based on \textit{Total Order} strategy.
@@
 
-We use the RankLib library\footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply Learning to Rank methods.
+We use the RankLib library\footnote{http://sourceforge.net/p/lemur/wiki/RankLib} to apply a large set of Learning to Rank methods.
 The library provides the  implementation of some Learning to Rank algorithms as well as evaluation measures in Java.
 By splitting the data in train, validation and test datasets, we use 5-Fold Cross-Validation on each run.
-One pointwise, three pairwise and two listwise methods are applied.
+One pointwise, three pairwise and two listwise methods are tested.
 
-Since evaluation of the results should be applied on whole the result list (with $3$ items), we have to use relevance grading evaluation measures like DCG, NDCG or ERR.
+Since evaluation of the results should be applied on  the entire result list (with $3$ items), we have to use relevance grading evaluation measures like DCG, NDCG or ERR.
 In the current study, NDGC and ERR both with rank position at $3$ are used.
 
-Because of the short final predicted list ($3$ items), every evaluator measure returns high result value even for a random ranker.
-This issue urges the need to run the evaluation on random data in order to find a baseline for comparison.
-We tackle the problem with two approaches.
+Because of the short final predicted list ($3$ items), every  measure returns a very high score.
+In order to understand the real benefit of our framework compared with just presenting the un-ranked set of three translators, we evaluate two random approaches.
 In the first approach, we run all the algorithms on data with random generated labels.

### 2014-04-17 docs/seminar/introduction.tex
more changes to all sections

@@
 In contrast to common expert retrieval systems, we include significant factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
-The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{http://github/anonymized}}.
+The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}.
 

### 2014-04-17 docs/seminar/methods.tex
more changes to all sections

@@
 
-\cite{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques.
+Cao and colleagues~\cite{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques.
 They were formalized as so-called \textit{candidate models} and \textit{document models}.
@@
 The document models first find documents relevant to the topic and then locate the experts associated with these documents \cite{er}.
+
+In either of the two models, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
+the final outcome, but instead an intermediary component.
+In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \cite{agg-learning}.
 
@@
 
-As well as ranking techniques, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
-the final outcome, but instead an intermediary component.
-In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \cite{agg-learning}.
+For the task at hand, we found that the two methods have to be used in two different steps.
+Aggregation can be used to bring together in one value elements essentially of the same nature.
+In this case - query similarity scores of different documents.
+The test collection at hand relies for its topical similarity exclusively on term frequencies, as there are no hyperlinks, metadata, or other sources of information in the documents.
+As a second step, in order to bring in attributes orthogonal to topical similarity, learning to rank methods are an obvious choice.
+In the following, we describe related work related to these two aspects, and in doing so prepare the ground for our experiments, which we present in the next section.
+
 \subsection{Aggregation Functions}
-The aggregation function has a significant impact on the performance of Expert Retrieval system.
+The aggregation function has a significant impact on the performance of Expert Retrieval system~\cite{agg-gp2}.
 As a usual scenario in expert retrieval systems, first each document related to an expert is scored and ranked regarding to query.
@@
 
-The effect of different features on the aggregation function is studied in \cite{agg-gp2}.
-They show that the number of documents is an important factor, such that the performance of different queries are optimal for different values of $N$.
+MacDonald and Ounis \cite{agg-vote} consider expert search as a voting problem, where documents vote for the candidates with relevant expertise.
+Eleven data fusion methods as well as three statistically different document weighting models were tested in their experiments.
+In practice, the approach considers both the number of documents and expert features regarding to the ranking score of the documents.
+The results show that while some of adapted voting techniques most likely outperform others, the proposed approach is effective when using the appropriate one.
+
+Cummins and colleagues~\cite{agg-gp2}  study the effect of different features on the aggregation function.
+They show that the number of documents is an important factor, in that the performance of different queries are optimal for different values of $N$.
 Comparing query-based features using statistical measures, they infer that the document features (such as TF, IDF) may not, in general, be able to predict the optimal number of documents to aggregate for each query.
@@
 
-\cite{agg-vote} looks to expert search as a voting problem, where documents vote for the candidates with relevant expertise.
-Eleven data fusion methods as well as three statistically different document weighting models were tested.
-In practice, the approach considers both the number of documents and expert features regarding to the ranking score of the documents.
-The results show that while some of adapted voting techniques most likely outperform others, the proposed approach is effective when using the appropriate one.
-
-Later on, focusing on related features discussed before \cite{agg-gp2} introduces a new aggregation method.
+Focusing on these features Cummins et al.
+\cite{agg-gp2} introduce a new aggregation method.
 It uses genetic programming to learn a formula for the weights of document associations within the candidate profiles.
-The formula denoted as $GP2$ is as follows:
+The formula, denoted as $GP2$, is as follows:
 
@@
 \subsection{Learning To Rank}
-Learning to rank refers to machine learning techniques for training the model in a ranking task.
+Learning to rank refers to machine learning techniques for training a model in a ranking task.
 Due to importance of ranking problems, learning to rank has been drawing broad attention in the machine learning community recently.
@@
 In the learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied.
-As \cite{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
+As Hang\cite{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
 
-One primitive step in accumulating data required for learning to rank, is relevance judgment normally done by human annotators. \cite{l2r-book} introduces three main strategies as follows.
+One primitive step in accumulating data required for learning to rank, is relevance judgments, normally done by human annotators.
+Lie \cite{l2r-book} presents the three main strategies in learning to rank:
 \begin{itemize}
@@
 Therefore, the group structure of ranking is ignored in this approach \cite{l2r-intro}.
-Linear or polynomial regression are widely used methods regarding to the approach.
+Here, linear or polynomial regression are widely used methods.
 
@@
 In fact, it cares about the relative order between two documents.
-Similar to the pointwise, the pairwise approach also ignores the group structure of ranking\cite{l2r-intro}.
+Similar to the pointwise approach, the pairwise method also ignores the group structure of ranking~\cite{l2r-intro}.
 Here is a brief explanation of some pairwise algorithms:
@@
 
-\cite{l2r-book} compares the algorithms by applying on different data-sets.
+Lie \cite{l2r-book} compares the algorithms by applying on different data-sets.
 It concludes that listwise techniques are in general the most effective among the others.
 However, the choice of the learning evaluation measure and the rank cutoff may have a noticeable impact on the effectiveness of the learned model \cite{l2r-when}.
+
+\subsection{Evaluation}
 
@@
 
-Recently, \cite{l2r-err} have proposed a new evaluation metrics called Expected Reciprocal Rank (ERR) which claims to model user's satisfaction with search results better than the DCG metric.
-\cite{l2r-err} addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it.
+Recently, Chapelle and Zhang~\cite{l2r-err} have proposed Expected Reciprocal Rank (ERR) which claims to model user's satisfaction with search results better than the DCG metric.
+Their work addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it.
 It asserts that based on research on modeling user click behavior \cite{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list.
 In other words, it assumes that a user is more likely to stop browsing if they have already seen one or more highly relevant documents.
-Introducing the ERR formula, \cite{l2r-err} claim that results reflect real user browsing behavior better and quantifies user satisfaction more accurately than DCG.
+Introducing the ERR formula, Chapelle and Zhang claim that results reflect real user browsing behavior better and quantifies user satisfaction more accurately than DCG.

### 2014-04-21 docs/seminar/casestudy.tex
cleaning repo + minor changes + order_aggregation data

@@
 \subsection{The Platform}\label{sec:platform}
-Essential components of the platform as well as the workflow of searching for the translators are depicted in Figure \ref{fig:architecture}.
+Essential components of the platform as well as the workflow of searching for the translators are depicted in Figure~\ref{fig:architecture}.
 The platform consists of four main components: \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiles}.
@@
 The proficiency score is obtained by aggregating the documents' similarity scores.
-Different aggregation functions are analyzed in Section\ref{sec:apply}.
+Different aggregation functions are analyzed in Section~\ref{sec:apply}.
 Finally, the \textit{Ranking} sub-system uses all the data generated in the previous steps to create the ranking model.
@@
 The assessment value can be from $1$ (very bad) to $5$ (perfect).
-In Section\ref{sec:apply} we use these assessments to evaluate and compare aggregation algorithms.
+In Section~\ref{sec:apply} we use these assessments to evaluate and compare aggregation algorithms.

### 2014-04-21 docs/seminar/evaluation.tex
cleaning repo + minor changes + order_aggregation data

@@
 
-Similar to \cite{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
+Similar ~\cite{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
 $GP2$ is the state of the art, while $Top1$ and $Top5$ are two common forms of $TopN$ aggregation algorithm which refers to algorithm that summarizes the $N$ top documents.
@@
 
-As input data we have 181 translation orders collected from the live system.
+As input data we have $181$ translation orders collected from the live system.
 For each of them, we know the translator who performed the translation (including all her previously translated documents), the text of the document to be translated, and the score given by the proof-reader.
 Because this is historical data, evaluating the aggregation method cannot be done by giving the same translation task to different translators.
-However, vy calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field.
+However, by calculating the value of each mentioned algorithm on all finished translations, we achieve three lists of translations each annotated with an additional aggregation value field.
 Then, in order to compare the algorithms, we test the correlation of each list with the list of translations annotated with proof-readers' assessments.
@@
 In order to calculate the correlation value, we applied Spearman Rank Order and Kendall Rank Correlation as two common methods.
-Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using the 181 records of purchased orders.
+Table~\ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using the $181$ records of purchased orders.
 In addition, it represents the Significance Test of both methods.
-For Spearman's test, p-values are computed using algorithm AS 89 \cite{as89}.
+For Spearman's test, p-values are computed using algorithm AS 89~\cite{as89}.
 
-As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kendall's.
+The coefficient value of Spearman is slightly higher than Kendall's.
 The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
-Regarding to p-Value of significance test shown in Table\ref{table:correlation}, a meaningful relation between GP2 and feedbacks can be considered.
-Top1 which has the worst values in the table shows a meaningless and near random correlation though.
+Regarding to p-Value of significance test shown in Table~\ref{table:correlation}, a meaningful relation between $GP2$ and feedbacks can be considered.
+$Top1$ which has the worst values in the table shows a meaningless and near random correlation though.
 
@@
 
-The result is shown in Table\ref{table:l2rresult}.
-Figure\ref{fig:l2rdiagram} depicts the corresponding data in diagrams.
+The result is shown in Table~\ref{table:l2rresult}.
+Figure~\ref{fig:l2rdiagram} depicts the corresponding data in diagrams.
 As it is shown, random values define a base line for comparison the goodness of methods.
@@
 In addition to comparing the methods, features comparison can be an interesting point.
-Table\ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model.
+Table~\ref{table:l2rcoefficient} shows the coefficients of features, calculated in Linear Regression model.
 The coefficient value is a measure for understanding the importance of each feature in comparison to the others.

### 2014-04-21 docs/seminar/introduction.tex
cleaning repo + minor changes + order_aggregation data

@@
 The remaining of the paper is organized as follows.
-In Section\ref{sec:casestudy}, the use-case is presented and the Translator-Expert Retrieval framework is described in detail.
-Then, Section\ref{sec:methods} explains the methods used in the study.
-Section\ref{sec:apply} shows the result of applied methods on the framework.
-We discuss these results and conclude the study in Section\ref{sec:conclusion}.
+In Section~\ref{sec:casestudy}, the use-case is presented and the Translator-Expert Retrieval framework is described in detail.
+Then, Section~\ref{sec:methods} explains the methods used in the study.
+Section~\ref{sec:apply} shows the result of applied methods on the framework.
+We discuss these results and conclude the study in Section~\ref{sec:conclusion}.

### 2014-04-21 docs/seminar/methods.tex
cleaning repo + minor changes + order_aggregation data

@@
 \label{sec:methods}
-With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval \cite{er-sparse}.
+With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval~\cite{er-sparse}.
 The goal of expertise retrieval is to link humans to expertise areas, and vice versa.
-In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er,er-community-aware}.
-The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005,er-community-aware}.
+In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query~\cite{er,er-community-aware}.
+The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects~\cite{trec2005,er-community-aware}.
 
@@
 The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query.
-The document models first find documents relevant to the topic and then locate the experts associated with these documents \cite{er}.
+The document models first find documents relevant to the topic and then locate the experts associated with these documents~\cite{er}.
 
@@
 the final outcome, but instead an intermediary component.
-In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \cite{agg-learning}.
+In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents~\cite{agg-learning}.
 
@@
 In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval.
-It refers to machine learning techniques for training the model in a ranking task \cite{er}.
-In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \cite{l2r-intro}.
+It refers to machine learning techniques for training the model in a ranking task~\cite{er}.
+In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it~\cite{l2r-intro}.
 
@@
 
-MacDonald and Ounis \cite{agg-vote} consider expert search as a voting problem, where documents vote for the candidates with relevant expertise.
+MacDonald and Ounis~\cite{agg-vote} consider expert search as a voting problem, where documents vote for the candidates with relevant expertise.
 Eleven data fusion methods as well as three statistically different document weighting models were tested in their experiments.
@@
 
-Focusing on these features Cummins et al.
-\cite{agg-gp2} introduce a new aggregation method.
+Focusing on these features Cummins et al.~\cite{agg-gp2} introduce a new aggregation method.
 It uses genetic programming to learn a formula for the weights of document associations within the candidate profiles.
@@
 In the learning to rank approach, the ranking problem is transformed to classification, regression and ordinal classification, and existing methods and techniques for solving machine learning problems are applied.
-As Hang\cite{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
+As Hang~\cite{l2r-intro} points out, the relation between learning to rank and ordinal classification is that, in ranking, one cares more about accurate ordering of objects, while in ordinal classification, one cares more about accurate ordered-categorization of objects.
 
 One primitive step in accumulating data required for learning to rank, is relevance judgments, normally done by human annotators.
-Lie \cite{l2r-book} presents the three main strategies in learning to rank:
+Lie~\cite{l2r-book} presents the three main strategies in learning to rank:
 \begin{itemize}
@@
 In the pointwise approach, the ranking problem is transformed to classification, regression or ordinal classification.
-Therefore, the group structure of ranking is ignored in this approach \cite{l2r-intro}.
+Therefore, the group structure of ranking is ignored in this approach~\cite{l2r-intro}.
 Here, linear or polynomial regression are widely used methods.
@@
 \begin{itemize}
-\item \textit{RankNet} \cite{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
-\item \textit{RankBoost} \cite{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.
-\item \textit{LambdaRank} \cite{l2r-lambdarank}: It considers the evaluation measures to set its pair weight.
+\item \textit{RankNet~\cite{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
+\item \textit{RankBoost}~\cite{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.
+\item \textit{LambdaRank}~\cite{l2r-lambdarank}: It considers the evaluation measures to set its pair weight.
 In particular, the evaluation measures (which are position based) are directly used to define the gradient with respect to each document pair in the training process.
-\item \textit{LambdaMART} \cite{l2r-lambdamart}: It combines the strengths of boosted tree classification and LambdaRank.
+\item \textit{LambdaMART}~\cite{l2r-lambdamart}: It combines the strengths of boosted tree classification and LambdaRank.
 \end{itemize}
 
-The listwise approach takes the entire set of documents associated with a query in the training data as the input and predicts their ground truth labels \cite{l2r-book}.
+The listwise approach takes the entire set of documents associated with a query in the training data as the input and predicts their ground truth labels~\cite{l2r-book}.
 In contradiction to two previous approaches, it maintains the group structure of ranking.
-In addition, ranking evaluation measures can be more directly incorporated into the loss functions in learning \cite{l2r-intro}.
+In addition, ranking evaluation measures can be more directly incorporated into the loss functions in learning~\cite{l2r-intro}.
 In the following, two common listwise algorithms are briefly discussed:
@@
 \begin{itemize}
-\item \textit{AdaRank} \cite{l2r-adarank}: It applies the evaluation measures on the framework of Boosting and focuses on effectively optimization.
-\item \textit{ListNet} \cite{l2r-listnet}: It uses different probability distributions in order to define the loss function.
+\item \textit{AdaRank}~\cite{l2r-adarank}: It applies the evaluation measures on the framework of Boosting and focuses on effectively optimization.
+\item \textit{ListNet}~\cite{l2r-listnet}: It uses different probability distributions in order to define the loss function.
 \end{itemize}
 
-Lie \cite{l2r-book} compares the algorithms by applying on different data-sets.
+Lie~\cite{l2r-book} compares the algorithms by applying on different data-sets.
 It concludes that listwise techniques are in general the most effective among the others.
-However, the choice of the learning evaluation measure and the rank cutoff may have a noticeable impact on the effectiveness of the learned model \cite{l2r-when}.
+However, the choice of the learning evaluation measure and the rank cutoff may have a noticeable impact on the effectiveness of the learned model~\cite{l2r-when}.
 
@@
 Their work addresses the underlying independence assumption of DCG that a document in a given position has always the same gain and discount independently of the documents shown above it.
-It asserts that based on research on modeling user click behavior \cite{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list.
+It asserts that based on research on modeling user click behavior~\cite{l2r-clickmodel1,l2r-clickmodel2}, the likelihood a user examines the document at rank $i$ is dependent on how satisfied the user was with previously observed documents in the ranked list.
 In other words, it assumes that a user is more likely to stop browsing if they have already seen one or more highly relevant documents.

### 2014-04-21 ciir/umass/edu/learning/RANKER_TYPE.java

@@ -1,14 +1,0 @@
-/*===============================================================================
- * Copyright (c) 2010-2012 University of Massachusetts.  All Rights Reserved.
- *
- * Use of the RankLib package is subject to the terms of the software license set 
- * forth in the LICENSE file included with this software, and also available at
- * http://people.cs.umass.edu/~vdang/ranklib_license.html
- *===============================================================================
- */
-
-package ciir.umass.edu.learning;
-
-public enum RANKER_TYPE {
-	MART, RANKBOOST, RANKNET, ADARANK, COOR_ASCENT, LAMBDARANK, LAMBDAMART, LISTNET, RANDOM_FOREST, LINEAR_REGRESSION, RANDOM_RANK
-}

### 2014-04-21 ciir/umass/edu/learning/RandomRank.java

@@ -1,67 +1,0 @@
-/*===============================================================================
- * Copyright (c) 2010-2012 University of Massachusetts.  All Rights Reserved.
- *
- * Use of the RankLib package is subject to the terms of the software license set 
- * forth in the LICENSE file included with this software, and also available at
- * http://people.cs.umass.edu/~vdang/ranklib_license.html
- *===============================================================================
- */
-
-package ciir.umass.edu.learning;
-
-import java.util.List;
-import java.util.Random;
-
-import ciir.umass.edu.metric.MetricScorer;
-
-public class RandomRank extends Ranker {
-
-	public RandomRank()
-	{		
-	}
-	public RandomRank(List<RankList> samples, int[] features, MetricScorer scorer)
-	{
-		super(samples, features, scorer);
-	}
-	public void init()
-	{
-		PRINTLN("Initializing... [Done]");
-	}
-	public void learn()
-	{
-		PRINTLN("--------------------------------");
-		PRINTLN("Training starts...");
-		
-		PRINTLN("---------------------------------");
-		PRINTLN("Finished sucessfully.");
-	}
-	public double eval(DataPoint p)
-	{
-		Random r = new Random();
-		return r.nextDouble();
-	}
-	public Ranker clone()
-	{
-		return new RandomRank();
-	}
-	public String toString()
-	{
-		return "";
-	}
-	public String model()
-	{
-		return "";
-	}
-	public void load(String fn)
-	{
-		
-	}
-	public void printParameters()
-	{
-		PRINTLN("NO PARAM");
-	}
-	public String name()
-	{
-		return "Random Rank";
-	}
-}

### 2014-04-21 ciir/umass/edu/learning/RankerFactory.java

@@ -1,116 +1,0 @@
-/*===============================================================================
- * Copyright (c) 2010-2012 University of Massachusetts.  All Rights Reserved.
- *
- * Use of the RankLib package is subject to the terms of the software license set 
- * forth in the LICENSE file included with this software, and also available at
- * http://people.cs.umass.edu/~vdang/ranklib_license.html
- *===============================================================================
- */
-
-package ciir.umass.edu.learning;
-
-import java.io.BufferedReader;
-import java.io.FileInputStream;
-import java.io.InputStreamReader;
-import java.util.HashMap;
-import java.util.List;
-
-import ciir.umass.edu.learning.boosting.AdaRank;
-import ciir.umass.edu.learning.boosting.RankBoost;
-import ciir.umass.edu.learning.neuralnet.LambdaRank;
-import ciir.umass.edu.learning.neuralnet.ListNet;
-import ciir.umass.edu.learning.neuralnet.RankNet;
-import ciir.umass.edu.learning.tree.MART;
-import ciir.umass.edu.learning.tree.LambdaMART;
-import ciir.umass.edu.learning.tree.RFRanker;
-import ciir.umass.edu.metric.MetricScorer;
-
-/**
- * @author vdang
- * 
- * This class implements the Ranker factory. All ranking algorithms implemented have to be recognized in this class. 
- */
-public class RankerFactory {
-
-	protected Ranker[] rFactory = new Ranker[]{new MART(), new RankBoost(), new RankNet(), new AdaRank(), new CoorAscent(), new LambdaRank(), new LambdaMART(), new ListNet(), new RFRanker(), new LinearRegRank(), new RandomRank()};
-	protected static HashMap<String, RANKER_TYPE> map = new HashMap<String, RANKER_TYPE>();
-	
-	public RankerFactory()
-	{
-		map.put(createRanker(RANKER_TYPE.MART).name().toUpperCase(), RANKER_TYPE.MART);
-		map.put(createRanker(RANKER_TYPE.RANKNET).name().toUpperCase(), RANKER_TYPE.RANKNET);
-		map.put(createRanker(RANKER_TYPE.RANKBOOST).name().toUpperCase(), RANKER_TYPE.RANKBOOST);
-		map.put(createRanker(RANKER_TYPE.ADARANK).name().toUpperCase(), RANKER_TYPE.ADARANK);
[…]

### 2014-04-21 ranker/ranker.java

@@ -1,9 +1,0 @@
-
-public class ranker {
-
-	public static void main(String[] args) {
-		// TODO Auto-generated method stub
-
-	}
-
-}

### 2014-04-21 runit.java

@@ -1,232 +1,0 @@
-import java.io.BufferedReader;
-import java.io.BufferedWriter;
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.FileReader;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.util.ArrayList;
-import java.util.List;
-import java.util.Random;
-
-import ciir.umass.edu.eval.Evaluator;
-import ciir.umass.edu.features.Normalizer;
-import ciir.umass.edu.features.SumNormalizor;
-import ciir.umass.edu.learning.RANKER_TYPE;
-import ciir.umass.edu.learning.RankerFactory;
-import ciir.umass.edu.metric.ERRScorer;
-import ciir.umass.edu.metric.MetricScorer;
-import ciir.umass.edu.metric.MetricScorerFactory;
-import ciir.umass.edu.utilities.MyThreadPool;
-import ciir.umass.edu.utilities.SimpleMath;
-
-
-public class runit {
-
-	public static void main(String[] args) throws IOException {
-		randomClassifier();
-			    
-	    //saveFile(loadFile(), 5);
-	}
-	
-	private static StringBuilder loadFile() throws IOException
-	{
-		BufferedReader br = new BufferedReader(new FileReader("l2r\\data\\train_standardized.letor"));
-		StringBuilder sb = new StringBuilder();
-		
-	    try {
-	    	String line1 = br.readLine();
-	        String line2 = br.readLine();
-	        String line3 = br.readLine();
-        
-	        while ((line1 != null) && (line2 != null) && (line3 != null)) {
-	        	int[] rndRank = getRandomRank();
-		        
-		        line1 = rndRank[0] + line1.substring(1);
-		        line2 = rndRank[1] + line2.substring(1);
-		        line3 = rndRank[2] + line3.substring(1);
-
-		        sb.append(line1);
-	            sb.append(System.lineSeparator());
-	            sb.append(line2);
-	            sb.append(System.lineSeparator());
-	            sb.append(line3);
-	            sb.append(System.lineSeparator());
-	            
-	            line1 = br.readLine();
-		        line2 = br.readLine();
-		        line3 = br.readLine();
-	        }
-	    } finally {
-	        br.close();
-	    }
-	    return sb;
-	}
-	
-	private static int[] getRandomRank()
-	{
-		int[] res = new int[3];
[…]

### 2014-04-21 scripts/correlations.R

@@ -1,0 +1,15 @@
+d <- read.csv("C:/Users/Navid/Google Drive/TUWIEN/2013W/Seminar/data/aggregation_data.csv", header=TRUE, sep = ",")
+gp2 <- as.numeric(unlist(d[1]))
+top5 <- as.numeric(unlist(d[3]))
+top1 <- as.numeric(unlist(d[2]))
+feedback <- as.numeric(unlist(d[4]))
+
+cor.test(feedback, gp2, method="spearman")
+cor.test(feedback, gp2, method="kendall")
+
+cor.test(feedback, top5, method="spearman")
+cor.test(feedback, top5, method="kendall")
+
+cor.test(feedback, top1, method="spearman")
+cor.test(feedback, top1, method="kendall")
+

### 2014-04-21 docs/seminar/evaluation.tex
new diagrams + repo cleaning (cont.)

@@
 Again, the assumption being that if we rank translation jobs by aggregation scores, the top elements would have high proof-reader scores, while the bottom elements lower scores.
+The distribution of data between the values of each aggregation function and the proof-reader's assessments is shown in Figure~\ref{fig:aggregationplot}.
 
-%mihai: put a plot here. On the X-axis the proof-reader scores and on the Y-axis the aggregation scores.
+\begin{figure}
+\centering
+\begin{subfigure}{.3\textwidth}
+  \centering
+	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_gp2.png}
+	\caption{GP2}
+\end{subfigure}%
+\begin{subfigure}{.3\textwidth}
+  \centering
+	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top5.png}
+	\caption{TOP5}
+\end{subfigure}%
+\begin{subfigure}{.3\textwidth}
+  \centering
+	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top1.png}
+	\caption{TOP1}
+\end{subfigure}
+\caption{Data distribution of aggregation values against proof-readers' assessments.
+Axes X shows the assessments of proof-readers.
+axes Y represents the values of the corresponding aggregation function}
+\label{fig:aggregationplot}
+\end{figure}
 
@@
 \begin{table}
-\begin{center}{
-\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
+\centering
 \begin{tabular}{c c|c|c|c|}
@@
 \end{tabular}
-}
+\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
 \label{table:correlation}
-\end{center}
 \end{table}
@@
 \begin{table}
-\begin{center}{
-\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
+\centering
 \begin{tabular}{|c|c|c|c|c|}
@@
 \end{tabular}
-}
+\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
 \label{table:l2rresult}
-\end{center}
 \end{table}
@@
 \begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{figures/l2rdiagram.png}
-\caption{Learning to Rank Results
-\label{fig:l2rdiagram}}
-\end{center}
+\centering
+\includegraphics[scale=0.6]{figures/l2rdiagram.png}
+\caption{Learning to Rank Results}
+\label{fig:l2rdiagram}
 \end{figure}
@@
 \begin{table}
-\begin{center}{
-\caption{Coefficient value of features in Linear Regression model}
+\centering
 \begin{tabular}{|c|c|}
@@
 \end{tabular}
-}
+\caption{Coefficient value of features in Linear Regression model}
 \label{table:l2rcoefficient}
-\end{center}
 \end{table}

### 2014-04-21 docs/seminar/methods.tex
new diagrams + repo cleaning (cont.)

@@
 \begin{itemize}
-\item \textit{RankNet~\cite{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
+\item \textit{RankNet}~\cite{l2r-ranknet}: Widely applied by commercial search engines, it uses gradient descent method and neural network to model the underlying ranking function.
 \item \textit{RankBoost}~\cite{l2r-rankboost}: It adopts AdaBoost algorithm for the classification over the object pairs.

### 2014-04-21 scripts/aggregation_plots.R

@@ -4,12 +4,10 @@ top5 <- as.numeric(unlist(d[3]))
 top1 <- as.numeric(unlist(d[2]))
 feedback <- as.numeric(unlist(d[4]))
 
-cor.test(feedback, gp2, method="spearman")
-cor.test(feedback, gp2, method="kendall")
+gp2_normalized = (gp2-min(gp2))/(max(gp2)-min(gp2))
+top5_normalized = (top5-min(top5))/(max(top5)-min(top5))
+top1_normalized = (top1-min(top1))/(max(top1)-min(top1))
 
-cor.test(feedback, top5, method="spearman")
-cor.test(feedback, top5, method="kendall")
 
-cor.test(feedback, top1, method="spearman")
-cor.test(feedback, top1, method="kendall")
+plot(feedback, gp2_normalized, xlab="", ylab="", pch=19)
 

### 2014-04-21 scripts/confidence_interval.R

@@ -1,0 +1,14 @@
+d <- read.csv("C:/Users/Navid/Documents/GitHub/expert-retrieval-translators/data/l2r_cv_results.csv", header=FALSE, sep = ",")
+i=5
+cv1<- as.numeric(d[i,3])
+cv2<- as.numeric(d[i,4])
+cv3<- as.numeric(d[i,5])
+cv4<- as.numeric(d[i,6])
+cv5<- as.numeric(d[i,7])
+
+
+x = c(cv1,cv2,cv3,cv4,cv5)
+
+d[i,1]
+d[i,2]
+t.test(x)

### 2014-04-21 scripts/l2r_plots.R

@@ -1,0 +1,32 @@
+d <- read.csv("C:/Users/Navid/Documents/GitHub/expert-retrieval-translators/data/l2r_results.csv", header=TRUE, sep = ",")
+algorithms <- unlist(d[1])
+evaluation_method<- unlist(d[2])
+evaluation<- as.numeric(unlist(d[3]))
+evaluation_random<- as.numeric(unlist(d[4]))
+
+cols <- c("algorithms"="#f04546","evaluation_method"="#3591d1","evaluation"="#62c76b","evaluation_random"="#62c76b")
+
+df <- data.frame(algorithms, evaluation_method, evaluation, evaluation_random)
+
+library(ggplot2)
+
+ggplot(df, aes(x=reorder(algorithms, -evaluation), fill=evaluation_method)) +
+geom_bar(aes(y=evaluation),
+	position=position_dodge(), 
+	stat="identity") +
+geom_line(aes(y=evaluation_random, 
+	group=evaluation_method),
+	colour="darkgreen",
+	lwd = 1)+
+geom_errorbar(aes(ymin=evaluation-.01, ymax=evaluation+.01), 
+	size=1,
+	width=.4,
+	position=position_dodge(.9))+
+xlab("") +
+ylab("") +
+ggtitle("") +
+theme_bw()+
+theme(legend.position="bottom",
+	axis.text.x = element_text(angle = 60, hjust = 1))+
+scale_fill_discrete("")+
+coord_cartesian(ylim = c(.3, 1))

### 2014-04-28 scripts/confidence_interval.R
aggregation plots

@@ -1,5 +1,5 @@
 d <- read.csv("C:/Users/Navid/Documents/GitHub/expert-retrieval-translators/data/l2r_cv_results.csv", header=FALSE, sep = ",")
-i=5
+i=12
 cv1<- as.numeric(d[i,3])
 cv2<- as.numeric(d[i,4])
 cv3<- as.numeric(d[i,5])

### 2014-04-28 scripts/l2r_plots.R

@@ -1,24 +1,25 @@
 d <- read.csv("C:/Users/Navid/Documents/GitHub/expert-retrieval-translators/data/l2r_results.csv", header=TRUE, sep = ",")
 algorithms <- unlist(d[1])
-evaluation_method<- unlist(d[2])
+methods<- unlist(d[2])
 evaluation<- as.numeric(unlist(d[3]))
-evaluation_random<- as.numeric(unlist(d[4]))
+cimin<- as.numeric(unlist(d[4]))
+cimax<- as.numeric(unlist(d[5]))
+random<- as.numeric(unlist(d[6]))
 
-cols <- c("algorithms"="#f04546","evaluation_method"="#3591d1","evaluation"="#62c76b","evaluation_random"="#62c76b")
 
-df <- data.frame(algorithms, evaluation_method, evaluation, evaluation_random)
+df <- data.frame(algorithms, methods, evaluation, cimin, cimax, random)
 
 library(ggplot2)
 
-ggplot(df, aes(x=reorder(algorithms, -evaluation), fill=evaluation_method)) +
+ggplot(df, aes(x=reorder(algorithms, -evaluation), fill=methods)) +
 geom_bar(aes(y=evaluation),
 	position=position_dodge(), 
 	stat="identity") +
-geom_line(aes(y=evaluation_random, 
-	group=evaluation_method),
+geom_line(aes(y=random, 
+	group=methods),
 	colour="darkgreen",
 	lwd = 1)+
-geom_errorbar(aes(ymin=evaluation-.01, ymax=evaluation+.01), 
+geom_errorbar(aes(ymin=cimin, ymax=cimax), 
 	size=1,
 	width=.4,
 	position=position_dodge(.9))+

### 2014-04-28 docs/seminar/introduction.tex
Merge branch 'CLEF2014' of https://github.com/neds/expert-retrieval-translators into CLEF2014
Conflicts:
	.gitignore

@@
 We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform.
-In contrast to common expert retrieval systems, we include significant factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
+In contrast to common expert retrieval systems, we include practical factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
 The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}.
+The contributions of the report are four-fold:
+\begin{enumerate}
+\item the application and adaptation of state-of-the-art IR methods to a new use-case
+\item extensive evaluation in a realistic scenario, including non-topical relevance criteria as part of the evaluation
+\item creation of a publicly available test collection
+\end{enumerate}
 

### 2014-04-29 docs/seminar/casestudy.tex
more changes

@@
 \subsection{Use-case}\label{sec:usecase}
-The user model for this application is that of an online user in possession of a document in a language other than the desired one.
+The user model for this application is that of an online user in possession of a document in a language other than a desired one.
 The need for a different language comes either from an internal need to know the contents of the document, or from an external requirement to provide the document in a high-quality translation in the desired language.

### 2014-04-29 docs/seminar/introduction.tex
more changes

@@
 This paper addresses the problem of searching translators as experts.
-We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform.
-In contrast to common expert retrieval systems, we include practical factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
-The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}.
+We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on a multilingual dataset.
+In contrast to common expert retrieval systems, we also include non-topical factors involved in the search for a translator (such as price and delivery time).% in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
+ The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators are studied; and a Learning-to-Rank phase in which different features are tested under different Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application, under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}.
 The contributions of the report are four-fold:
@@
 \item extensive evaluation in a realistic scenario, including non-topical relevance criteria as part of the evaluation
-\item creation of a publicly available test collection
+\item creation of a publicly available test collection for both of the steps involved in the retrieval framework
 \end{enumerate}
 
-The remaining of the paper is organized as follows.
-In Section~\ref{sec:casestudy}, the use-case is presented and the Translator-Expert Retrieval framework is described in detail.
+The remainder of the paper is organised as follows: In Section~\ref{sec:casestudy}, the use-case is presented and the Translator-Expert Retrieval framework is described in detail.
 Then, Section~\ref{sec:methods} explains the methods used in the study.

### 2014-04-29 docs/seminar/methods.tex
more changes

@@
 
-One primitive step in accumulating data required for learning to rank, is relevance judgments, normally done by human annotators.
+The first step in accumulating data required for learning to rank, is relevance judgments, normally done by human annotators.
 Lie~\cite{l2r-book} presents the three main strategies in learning to rank:
@@
 
-Among the three mentioned kinds of judgments, the first one is the most popularly used judgment since is the easiest to obtain. While the third one is more accurate but laborious for human annotators.
+Among the three mentioned kinds of judgments, the first one is the most popularly used judgment since is the easiest to obtain, while the third one is more accurate but laborious for human annotators.
+In our case, we have used the total order method because our ranked lists consisted of only 3 translators.
 
@@
 
-A critical point in all kinds of information retrieval systems is the evaluation of results.
+A critical point in all information retrieval systems is the evaluation of results.
 The evaluation on the performance of a ranking model is carried out by comparison between the ranking lists output of the model and the ranking lists given as the ground truth.

### 2014-04-29 docs/seminar/evaluation.tex
more changes
more changes
still to do: fit it to 12 pages, re-write conclusion

@@
   \centering
-	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_gp2.png}
+	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_gp2.png}
 	\caption{GP2}
@@
   \centering
-	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top5.png}
+	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top5.png}
 	\caption{TOP5}
@@
   \centering
-	\includegraphics[width=0.8\textwidth]{figures/aggregation_plots_top1.png}
+	\includegraphics[width=0.99\textwidth]{figures/aggregation_plots_top1.png}
 	\caption{TOP1}
 \end{subfigure}
+\vspace{-0.3cm}
 \caption{Data distribution of aggregation values against proof-readers' assessments.
@@
 \label{fig:aggregationplot}
+\vspace{-0.3cm}
 \end{figure}
@@
 \begin{table}
+\vspace{-0.3cm}
 \centering

### 2014-04-30 scripts/confidence_interval.R
correcting l2rdiagram + adding data

@@ -1,5 +1,5 @@
 d <- read.csv("C:/Users/Navid/Documents/GitHub/expert-retrieval-translators/data/l2r_cv_results.csv", header=FALSE, sep = ",")
-i=12
+i=14
 cv1<- as.numeric(d[i,3])
 cv2<- as.numeric(d[i,4])
 cv3<- as.numeric(d[i,5])

### 2014-04-30 scripts/l2r_plots.R

@@ -14,10 +14,11 @@ library(ggplot2)
 ggplot(df, aes(x=reorder(algorithms, -evaluation), fill=methods)) +
 geom_bar(aes(y=evaluation),
 	position=position_dodge(), 
-	stat="identity") +
+	stat="identity",
+	colour="black") +
 geom_line(aes(y=random, 
 	group=methods),
-	colour="darkgreen",
+	colour="black",
 	lwd = 1)+
 geom_errorbar(aes(ymin=cimin, ymax=cimax), 
 	size=1,
@@ -29,5 +30,6 @@ ggtitle("") +
 theme_bw()+
 theme(legend.position="bottom",
 	axis.text.x = element_text(angle = 60, hjust = 1))+
-scale_fill_discrete("")+
-coord_cartesian(ylim = c(.3, 1))
+coord_cartesian(ylim = c(.3, 1))+ 
+scale_fill_manual(values=c("white", "darkgray"))+
+opts(legend.title=theme_blank())

### 2014-05-04 docs/seminar/conclusion.tex
revising
changed some small stuff in other places, but mostly in conclusion

@@
+%\vspace{-0.2cm}
 \section{Conclusion and Future Work}
+%\vspace{-0.2cm}
 \label{sec:conclusion}
-In the paper, we put forward a comprehensive solution for implementation and design of a translator-expert retrieval system.
-As well as system architecture, we thoroughly study the obstacles and pitfalls in implementation of such a system.
-Document aggregation as well as ranking problems are two main issues thoroughly discussed in the paper and followed by provided solutions.
+We propose a comprehensive solution for a translator-expert retrieval system.
+As well as system architecture, we thoroughly study the obstacles and pitfalls in implementing such a system.
+Multilingual IR tools are adapted to solve two essential steps in a practical system: Estimating the translators proficiency on a particular topic (document aggregation), ranking translators based on real-world factors (learning to rank).
+%as well as ranking problems are two main issues thoroughly discussed in the paper and followed by provided solutions.
 
-The first issue concerns with the comparison of the aggregation methods.
+To address the first issue we have compared three commonly used aggregation methods.
 The aggregation methods estimate the proficiency of each translator based on the similarity values of the previous translated documents with the query document.
 Using the assessment of the proof-readers on the final translation as the golden data, we compare three aggregation methods.
-Finally, GP2 method shows better performance in comparison to the others with reasonable good results.
+We found that the GP2 method shows better performance in comparison to the others with reasonable good results.
+Future work in addressing the estimation of translators' proficiency will allow us to increase the correlation between the aggregation and proof-readers' scores.
 
 The second issue tackles the problem of experts ranking.
-By applying different learning to rank algorithms, we obtain a ranking model based on linear regression with fairly good performance.
-The model's performance is approved by both NDCG and ERR evaluation measures.
-Feature analysis of data indicates the importance of price and delivery time in comparison to the other features for the the human annotators.
+By applying different learning to rank algorithms, we obtain a ranking model based on linear regression with a very high performance.
+The model's performance is tested with both NDCG and ERR evaluation measures.
+Feature analysis of data shows that real users consider  price and delivery time much more important than the other features.
+This is relatively disappointing, but in retrospective not surprising for a real-world system.
 
-Recently, different aspects of expert retrieval platforms drawing an increasing interest.
+%Recently, different aspects of expert retrieval platforms drawing an increasing interest.
 Based on the current study, we aim to accomplish a comprehensive aggregation method regarding to the translation context in the following studies.

### 2014-05-04 docs/seminar/evaluation.tex
changed some small stuff in other places, but mostly in conclusion

@@
 \caption{Data distribution of aggregation values against proof-readers' assessments.
-Axes X shows the assessments of proof-readers.
-axes Y represents the values of the corresponding aggregation function}
+The x-axis shows the assessments of proof-readers, while the y-axis represents the values of the corresponding aggregation function}
 \label{fig:aggregationplot}
@@
 \vspace{-0.3cm}
+\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
 \centering
@@
 \end{tabular}
-\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
 \label{table:correlation}
+\vspace{-0.3cm}
 \end{table}
@@
 \subsection{Learning To Rank}
+\vspace{-0.2cm}
 In order to accumulate data required for ranking model, we conduct a survey with eight human annotators.
@@
 \vspace{-0.3cm}
+\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
 \centering
@@
 \end{tabular}
-\caption{Results of applying Learning to Rank methods based on NDCG and ERR evaluation measures}
+\vspace{-0.3cm}
 \label{table:l2rresult}
@@
 \includegraphics[scale=0.6]{figures/l2rdiagram.png}
+\vspace{-0.3cm}
 \caption{Learning to Rank Results}
@@
 \vspace{-0.3cm}
+\caption{Coefficient value of features in Linear Regression model}
 \centering
@@
 \end{tabular}
-\caption{Coefficient value of features in Linear Regression model}
 \label{table:l2rcoefficient}

### 2014-05-04 docs/seminar/evaluation.tex
minor changes

@@
 
-The coefficient value of Spearman is slightly higher than Kendall's.
-The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers.
-Regarding to p-Value of significance test shown in Table~\ref{table:correlation}, a meaningful relation between $GP2$ and feedbacks can be considered.
+The outcome shows an approximately weak correlation between aggregation functions and assessments of proof-readers.
+In all the algorithms, the coefficient value of Spearman is slightly higher than Kendall's.
+Regarding to p-Value of significance test, a meaningful relation between $GP2$ and assessments can be considered.
 $Top1$ which has the worst values in the table shows a meaningless and near random correlation though.
@@
 \vspace{-0.3cm}
-\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks as well as P-Value of Significance of Correlation Test}
 \centering
@@
 \end{tabular}
+\caption{Correlation test between algorithms and proof-readers' assessments as well as P-Value of significance of correlation test}
 \label{table:correlation}

### 2014-05-15 docs/paper/casestudy.tex
Corrections + renaming the paper folder

--- 2014-04-29 docs/seminar/casestudy.tex
@@
 It uses Learning to Rank techniques to return the most relevant candidate translators.
-The training data is provided by a group of annotators  familiar with the business of the company, using an evaluation system created specifically for this generating this ground truth.
+The training data is provided by a group of annotators  familiar with the business of the company, using an evaluation system created specifically for generating this ground truth.
 The evaluation system presents three translators and the annotators rank them based on the values of each of their attributes (i.e.

### 2014-05-15 docs/paper/evaluation.tex
Corrections + renaming the paper folder

--- 2014-05-04 docs/seminar/evaluation.tex
@@
 
-Similar ~\cite{agg-gp2}, we compare three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
+We repeat the experiment done by Cummins and colleagues~\cite{agg-gp2} for the particular use-case and data at hand, comparing three aggregation algorithms: $GP2$, $Top5$ and $Top1$.
 $GP2$ is the state of the art, while $Top1$ and $Top5$ are two common forms of $TopN$ aggregation algorithm which refers to algorithm that summarizes the $N$ top documents.
@@
 \vspace{-0.3cm}
+\caption{Correlation test between algorithms and proof-readers' assessments as well as P-Value of significance of correlation test}
 \centering
@@
 \end{tabular}
-\caption{Correlation test between algorithms and proof-readers' assessments as well as P-Value of significance of correlation test}
 \label{table:correlation}
@@
 Among the applied methods, Linear Regression and LambdaMART tend to have better results.
+In particular, Linear Regression shows a narrower confidence interval and hence more stable.
 Furthermore, tracing NDCG and ERR diagrams shows a considerable similarity in behavior of both evaluation methods regarding to the data.

### 2014-05-15 docs/paper/paper.tex
Corrections + renaming the paper folder

\input{config}

\begin{document}
\title{Real-world Translator Retrieval Framework}

\author{Navid Rekabsaz\inst{1} \and Mihai Lupu\inst{2}}
%
\authorrunning{Navid Rekabsaz et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Navid Rekabsaz, Mihai Lupu}
%
\institute{Faculty of Informatics, Vienna University of Technology\\
\email{navid.rekabsaz@student.tuwien.ac.at}
\and
Information and Software Engineering Group
Vienna University of Technology\\
A-1040 Vienna, Austria
\email{lupu@ifs.tuwien.ac.at}}

\maketitle

\begin{abstract}
%\boldmath
\input{abstract}
\end{abstract}

\input{introduction}
\input{casestudy}
\input{methods}
\input{evaluation}
\input{conclusion}

\bibliographystyle{splncs}
\bibliography{paper}

\end{document}

### 2014-07-01 docs/paper/introduction.tex
Corrections + renaming the paper folder
camera-ready version

--- 2014-04-29 docs/seminar/introduction.tex
@@
 We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on a multilingual dataset.
-In contrast to common expert retrieval systems, we also include non-topical factors involved in the search for a translator (such as price and delivery time).% in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
- The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators are studied; and a Learning-to-Rank phase in which different features are tested under different Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application, under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}.
-The contributions of the report are four-fold:
+In contrast to common expert retrieval systems, we also include non-topical factors involved in the search for a translator (such as price and delivery time).
+% in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document.
+The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators are studied based on the proof-readers' assessments as gold standard; and a Learning-to-Rank phase in which different features are tested under different Learning-to-Rank methods based on a manually created ground truth, which we make available together with the gold standard and the document similarities, under GPL\footnote{\url{https://github.com/neds/expert-retrieval-translators}}.
+The contributions of the report are three-fold:
 \begin{enumerate}
+\vspace{-0.3cm}
 \item the application and adaptation of state-of-the-art IR methods to a new use-case
@@
 \item creation of a publicly available test collection for both of the steps involved in the retrieval framework
+\vspace{-0.3cm}
 \end{enumerate}
